Welcome all, to \textbf{Picocon 41}!

For this year’s event, we’re bringing it all back to the beginning. When you were just a wee toddler (fine, a medium-sized teenager), what was it that drew you to the fold of science fiction and fantasy? Was it the thrill of what could be, if the world matched up to one’s imagination? The dread of what could be, if today’s world was tweaked just a little? Honestly, yeah, but that’s beside the point. The biggest attraction by far to the uninitiated will always be the beasties, whether they’re monstrous horrors or cute-n-cuddlies (or both, in the case of Sophie Number Five).

A magical menagerie deserves the finest presenters, and I’m proud to announce this year’s Guests of Honour: four incredible authors talking about their own creatures, and how they set them loose on the page. Whether you’re interested in spinecrawling monsters or mechanical elephants, diving dragons or crimson cranes, you’re sure to be entertained.

If you can make it through the day without being devoured by Kraky, you’ll be sure to enjoy our wholesome traditions of death and destruction (of Dodgy Merch) and horrors beyond comprehension (Turkey Talks). We’ll also be carrying out a more recent tradition of Baguette Battles, out of sensitivity to our resident mermaids, and out of love for the local pigeons. Finally, our all-day Scavenger Hunt and Picocon Quiz at the end of the evening will give you the chance to make your chosen mascot proud.

Thank you for attending this year’s Picocon, and enjoy The Menagerie; ask yourself what the best mythical creature is, and why it’s the Loch Ness Monster.