Ah. Once again you find yourself trapped in one of the machinations devised by the Imperial Science Fiction Society --- Picocon. A newcomer, you say? Fear not, for this handbook shall guide you through the perils of the day...

Through the powers of divination and meticulous planning, we shall be graced with the presence of not one, but four, \emph{Guests of Honour}. After lecturing us on the wonders and horrors of these creatures of our design, there shall be a \emph{Guest Panel} where all your questions shall be answered, followed by some book signings. 

After lunch, there shall be righteous \emph{Destruction of Dodgy Merchandise}. The audience (You) shall be given a choice: to save one of these pitiful creations from a fate of total annihilation; or, to bring the hammer of justice (and the cold death of --196 C) down on their stupid little faces. The choice is yours.

In conjunction with this, one shall bear witness to the height of modern chivalry --- \emph{Baguette Bash}. Engage in duels of honour, and destroy your enemies with sticks of rolled bread, or sit on the sidelines and enjoy the show, but only if you are a coward.

The dreaded \emph{Turkey Talks} shall once again be held. Introverts will, for some ineffable reason, willingly choose to speak on stage. The audience shall be given the power to prolong the fool's suffering, in form of charitable donations.

\emph{Imperial Tabletop \& Gaming} will return once more in \emph{Femtocon}. They are cool too, so definitely check out their society as well. As always, those who brave the depths of science fiction and fantasy are always welcome to visit the \emph{Sci-Fi Library}, open lunchtimes throughout the week in Beit's West Basement.

As written.
