Denizens of Imperial College, greetings, and welcome to the Imperial College Science Fiction and Fantasy Society! I, your humble Chair Entity, extend a celestial welcome to both newcomers and seasoned travellers alike.

Our Fortress of Solitude (also known as the Sci-Fi Library) can be found in the West Basement of Beit, where we've managed to cram in a hoard of ten thousand books and three thousand DVDs. The proverbial gates are open every lunchtime during the week (Monday to Friday) from 12-2pm, and all are welcome to seek refuge within our sanctuary, whether it's to make use of our collection, socialise, or just relax before an afternoon of studying.

Our roster of events includes our typical gatherings on Friday evenings (movie marathons, game nights, the occasional seasonal event), as well as subsidised cinema trips to see the latest sci-fi and fantasy releases. Look forward to our upcoming trip to see \textit{The Ballad of Songbirds and Snakes}, and our Christmas Party / Dr Who double feature, promising seasonal merriment and time-travelling revelry. And let's not forget our own annual convention, Picocon, looming on the horizon.

You'll probably hear this a lot, but I must say again: Ten. Thousand. Books. If there’s a series you're wanting to get into, chances are we already have it, and you’re welcome to come lend anything we have (though you’ll need membership first). And if not, feel free to submit a library request!

So, if you're searching for a community with a shared love of all things science fiction and fantasy, then look no further. We're a friendly bunch (I promise we're not a cult), and no one bites\footnotemark[2]{}.
