This should give you a taste of what kind of things we have in store
this term. To keep yourself up to date, join our mailing list or whats-app (or both I'm not going to stop you).

\textbf{Lunchtime Showings} ---
If you didn't know already, we have a library in the west basement of Beit!! Every lunchtime, it is kindly opened to the general public by whichever member of the committee happens to placate the machine spirit in the door card reader. It consistently opens between 12 and 2pm, so if you want to check out the massive collection of books and films (over 10000 books and 3000 films!! And any that we don't have you can request using the form on our whatsapp, as long as you have membership) or just hang out with a group of nerds and chat feel free to show up! No need to have membership, so you can try before you buy. Follow the instructions on the last page to get here.

\textbf{Cinema Trips} ---
Come along as we go out as a group to see the latest fantasy and
sci-fi hits in cinema, with tickets often discounted for members. The final one this term will be to The Ballad of Songbirds and Snakes, the new Hunger Games movie, where I am assured that people are hungry and gaming, there is a ballad, songbirds may feature and snakes are decently likely to show up. We will get pizza beforehand, so if you want pizza and a cinema ticket for just £4, follow our instagram or our mailing list, linked here or there are QR codes in the library (see above).


\textbf{Secret Santa!} ---
We are running a secret santa! Enter your name into the hat by the 1st of December, and you will be assigned to buy someone a gift under £10! Someone will also be assigned to you, but you will not know who. So normal Secret Santa rules, really. And they will be given back in...


\textbf{Christmas Party Dr Who day!!} ---
This year, the Christmas party has happened to fall upon the anniversary of the ambiguous doctor! This double feature will span the length of Saturday afternoon, the 9th of December, starting at 4pm and going til late, so come if you like Christmas, Dr Who or any combination of the above! We will have christmassy snacks, Cthulhu-based carols, Dr-Who related TV and between 15 and 25 other nerds.
