Greetings! Welcome to the \textit{important} part of \textit{Wyrmtongue}. I’m your host, The Sofa, and will be responsible for this year’s Picocon event along with our Beanbag, Kai Lam. Picocon is our society’s annual convention, celebrating science-fiction and fantasy that’s been running since Orwell’s most famous book title, and this academic year will be the \nth{41} in the series. Picocon serves multiple purposes: bringing a spotlight to authors in the genre, raising funds for both the society and charity, and just being a fun event where current members can socialise and meet alumni. 

The theme of Picocon 41 is \textit{The Menagerie}! That’s magical creatures and beasts existing only in the imagination, all humanely caught and trapped for your entertainment some time in March 2024. We’re talking big scary reptiles, mysterious sea creatures, slightly unusual mammals, chickens on fire – and is that an alien!? Well, you’ll have to keep up with us on social media and check out the Picocon fanzine to learn the names and faces. If you have your own addition to the menagerie, contact us electronically or in the library at lunchtime and we’d love to meet your own magical pets. 

Picocon 41 doesn’t yet have an official date – for now. Expect a definite date by January 2024, and until then development will all be behind the scenes to create a fun and unique event. You can still expect the Picocon classics: Guests Of Honour giving presentations and speeches, Destruction of Dodgy Merchandise with a comically large mallet, and Turkey Talks where money \textit{really} talks. As of \textit{Picocon 40: Twisted}, Baguette Battles are replacing the notorious Fish Fights of yore. Same silliness, but lighter on the biological warfare. So be there – you won’t regret it! 

Enjoy the rest of term, and try not to get mauled by a gryphon on your way to lectures. 
