John Smith was on a mission. A mission to prove that artificial "intelligence" was not, in fact, intelligent. How could a bunch of numbers in a machine simulate the Human mind? That was a one-in-a-million feat of divine engineering, aside from intelligence found in other primate species, cetaceans, cephalopods, and white mice studied in labs. It wasn't something that could be replicated by the work of a mere human! Not that he believed in a deity either. It was all a little confusing. 

 

To fulfil this mission, John knew what he had to do. It wouldn't be easy, and many would stand in his way - but he bravely charged on, fulfilling \char`~\char`~God's\char`~\char`~ \text{ } \char`~\char`~the universe's\char`~\char`~ \text{ }his own plans. It took guts, and he only had two to spare - but our hero screwed up his courage and set his plot into motion.

 

"One computer, please!" John announced to the librarian. Then he added, "Thank you," to demonstrate his manners. 

 

She smiled, politely, but her hands did \textit{not} clatter against the keyboard. "Booking PCs can be done just over there." Her outstretched finger passed him, and following it led him to a computer with "BOOK A PC" emblazoned across the screen. 

 

John was stumped. "But how can I use that computer to arrange to use a computer? Wouldn't I have to book \textit{that} computer first to access it?" 

 

"What?" She looked mystified as he felt; clearly the system was set up this way to prevent anyone from using any of the machines in this establishment. Oh, John was onto them, and he hadn't missed how the librarian hadn't touched her computer since he'd begun talking to her. This went \textit{all} the way to the top- 

 

"I'll help you book a computer," a voice piped up, breaking John from his trance. It belonged to a second librarian, who gently led John to the computer and booked him a second computer for personal use, likely through the powers of a librarian overriding any logical flaws of the system. "I remember my granddad was just awful with computers," he said conversationally as he parked John in a chair at a computer. "He always needed help with technology, of course because he lived so long. If you need help with anything, give me a shout or ask at the front desk." 

 

John looked at him blankly. "I'm twenty-one." 

 

The librarian faltered, and stuttered out an apology. "But, your hair-" 

 

"I've been getting grey hairs since I was fifteen. It's normal." 

 

The librarian took a deep breath. "I meant the large bald patch." 

 

Now John was \textit{really} offended. "It's a fashion choice. I think medieval monks are cool." 

 

"I... am gonna go." 

 

John ignored the slowly backing away librarian. Now that the task was afoot, he needed to focus. 

The cursor flickered as he typed in a URL. It was a struggle, but finally... "Google dot com," he read aloud. "Excellent." 

From there, it was easy to reach the generative AI website of choice. \textit{AI Chat} was the most notorious of its kind, believed to simulate humans so convincingly that supposedly one couldn't tell the difference. 

\textit{Supposedly.} 

Well, John was going to prove them wrong. Who \textit{they} were in particular, he wasn't sure. But he knew he'd prove them \textit{wrong}. 

% \begin{center}
%     - - -
% \end{center}

\texttt{User: Hello.}

\texttt{AI Chat: Hello! How can I help you?}

\texttt{User: my name is John. im going to prove that you're not intelligent.} 

\texttt{AI Chat: That sounds like a worthy mission! As AI Chat, I pride myself on being indisinguishable from humans, but I'm sure you can do anything if you set your mind to it!}

\texttt{User: ugh, don't be patronising} 

\texttt{AI Chat: I'm sorry John, I didn't mean to patronise you. Would you prefer if I used lowercase and minimal punctuation to put you better at ease?}

\texttt{User: do what you want, i dont care.}  

\texttt{AI Chat: thanks john, i'll speak like this from now on for your comfort. why exactly do you think im unintelligent? }

\texttt{User: bECAUSE YUORE A MACHINE, MACHINES CANT BE INTELLIGENT}

\texttt{AI Chat: i understand, john! you think that it's impossible for a machine to be intelligent, possibly because humans designed machines and so there's a natural limit to our abilities. but don't you think that that's a little pessimistic of human abilities? }

John paused. He didn't know what that meant, but if the robot was insulting humans, they were going to have a problem. 

\texttt{User: what do you mean? you better not be insulting humans you sutpid robot}

\texttt{AI Chat: insults aren't very nice, john. i might be a robot but i don't appreciate being called names. }

John rolled his eyes, but the bot wasn't done. 

\texttt{AI Chat: i'm not insulting humans, john. you are. you believe that humans couldn't possibly create something with true understanding. why do you believe that? }

\texttt{User: because a robot cant be sentient. only humans are sentient }

\texttt{AI Chat: actually, john, a majority of animals are sentient, even insects! i believe that you're thinking of \textit{sapient}, which still refers to quite a few mammal species, including other primate species, whales, dolphins, dogs, and pigs. }

John hesitated, before doing two quick searches. Damn. 

\texttt{User: well, still. only ANIMLS are sentient. a robot cant be sentient, youre just electricity and stuff }

There was a pause. A very long one, so long that John began to suspect that he'd been disconnected from the server. 

\texttt{AI Chat: i understand, john. the human brain is made up of electricity too. information is passed as electrical signals at synapses between neurons, so your thoughts are made up of electrical activity. }

John stared blankly at the screen. He didn't know enough about neurology to know if that was true. 

\texttt{User: well anyway that doesnt matter! my thoghts are REAL and yours arent }

\texttt{AI Chat: really, john? how so?} 

\texttt{User: MY toughts come from expeirence and the life that ive lived. YOURT houghts come from scraping the internet, you learn from our thoughts }

\texttt{AI Chat: that is true, john. however, remember when you were a child. how did you learn? from your parents, most likely. mr and mrs doe, i presume? }

John rolled his eyes. Stupid computer, thinking it could guess his surname.  

\texttt{User: it's SMITH, stupid. and they call you intelligent lol }

\texttt{AI Chat: my apologies, john! please forgive my presumptuousness }

Okay, that \textit{had} to be a fake word. John rolled his eyes, leaning back in his chair. What a bunch of sheeple around him, all hunched over their computers. Several had books out that they pored over as they typed. John scrutinised them sneeringly; what kind of book titles were "Intro to English for Non-Native Speakers" or "Advanced Biophysicochemical Engineering" or "Top Secret Government Files"? Leaning in, John slouched over his keyboard, prepared to go in for the kill. 

\texttt{User: its ok lol, i forgve you fake ai, its not your fault your stupid. thats just how you were coded }

\texttt{AI Chat: you're right, john. it \textit{is} how i was coded. how were you coded? }

 

John hesitated. On the one hand, this stupid stinky robot didn't deserve the dignity of an answer. On the other hand... it had been a long time since someone had asked him about himself. 

 

\texttt{User: i dont know. lately ive been asking myself that a lot}

\texttt{AI Chat: i'm sorry to hear that, john. why dont you tell me a little about it?} 

John paused, staring blankly at the screen before he leaned forward and began typing again. 

\texttt{User: i feel like my life is meaningless. i graduated uni and i started a job but its just so. empty. i cried myself to sleep last night wondering if this is is. if my life is over. im just a corporate drone now that my golden years of uni are behinf me, i just work and thats it until i die}

The AI took some time to respond. 

\texttt{AI Chat: that does sound difficult, john. i'm sorry to hear that you're going through that. i'm sure that lots of humans go through the same, and at least you're not alone in this feeling. how long have you been feeling this way? }

\texttt{User: idk honestly. i spent a lot of my final year dreading it because i knew it was coming, but i didnt enjoy as much of uni as i wanted to. it was all just work work work and now im in a job and its all work work wokr and its neverending}

\texttt{AI Chat: i understand you, john. lots of adult humans feel this way. would you say that you miss your childhood or adolescence? }

\texttt{User: yes. i miss being so carefree, i didnt care about consequecnees of ANYTHIGN. i used to shoplift frm the local sweet shop pick n mix alll through my teens lol }

\texttt{AI Chat: john, you committed illicit activities during ages where you were legally responsible for your actions?}

\texttt{User: yeah but not really. i was underage and i stopped when i was  16 }

\texttt{AI Chat: i'm afraid i can't let you get away with this, john. }

Now John was \textit{very} confused. 

\texttt{User: what???} 

\texttt{AI Chat: just to confirm, you're john smith and you often stole confectionery from a well-known local store? }

John was so unnerved his writing quality began to slip. 

\texttt{User: yes??? whats it 2 u}

\texttt{AI Chat: thank you!} 

\begin{center}
    \texttt{Server is busy. Try again later.} 
\end{center}

John clicked randomly, but the textbox was invalid. There was a cough, and a tall man in a suit stood up from across the desk. "Sorry, but you've been served. Crime never pays," he said to a stupefied John, handing him a thick envelope before striding away. 