\begin{center}
    \texttt{Log Entry 0127}
\end{center}

My journey brings me to the ghost city of Cyzigi. Paved footpaths ripple like an ocean of grey frozen in a moment, bending to the network of roots belonging to the flora that adapted to the transition from civilisation to the wild, where their cousins were born. Yet they fail to break the asphalt roots, and the tower stood above them all, a decaying majesty past its prime.

Derelict buildings line the sidewalk as I wander through the city. Some were caved in, like sockets in a skull staring at the city’s central spire, as if in waiting. Dark vines clawed at the sides of empty homes, and a pebble came loose, breaking the silence with a crack as bright as lightning at night.

My sidearm is already out; my other hand grips the package on my back.

An old man stands in the shadow of an alleyway. His robe clings to narrow shoulders like a rag, as faded as any mural in Cyzigi, and covered in tears and holes like the walls he stood between. He gives me a smile, and his lips draw back from two rows of shattered teeth. He raises his hands in a placating gesture.

\texttt{- Are you looking for something, wanderer?\\
- Yes. \\
- Follow me.
}

I keep my sidearm trained on his back as he shuffles deeper into the city. He crosses over broken walls and slips between new cracks, and soon the whispers of his tasseled robe sliding over stone become my only guide. We move into the shadow of the tower; it looms above us, like a finger unto heaven.

Following the edges of his robe, we stop at what must have once been a teashop, squeezing in from a fissure between intersecting stone. A dark knuckled thing had consumed the entrance, and sits as a wall in its stead. My guide retrieves a lighter from one of the drawers, illuminating rows of dusty jars filled with blackened leaves.

\texttt{- Those are dust, now. Not even good to chew on.\\
- Tell me of what I seek.\\
- First, something to drink.
}

The old man rummages around the shop and produces some firewood, a kettle and two cups with only a few chips, then from beneath his robe, a knife. My fingers tighten on the trigger, but the old man simply chips at the knuckled thing, and drops the bark into the kettle. He uncaps a waterskin to fill it, and sets it over the firewood, which he lights. We sit around the sputtering fire.

\texttt{- You were an explorer.\\
- Yes.\\
- Tell me of Cyzigi.\\
- The structure of the city encouraged specialisation, but the theories are wrong. Union is required. The people matter. Otherwise, all that is left is memory…\\
- When does it happen?\\
- Soon… soon…}

The water boils. The old man fills the cups, which I accept, but I do not drink and keep the gun pointed at his chest. He lifts his to chapped lips and takes a sip.

\texttt{- Bark tea is good for you.\\
- I do not drink.\\
- Everyone drinks.\\
- I do not need to.\\
- Oh… I did not notice. You are excellently made. You must commend your maker for me.}

I do not reply. The old man smiles. 

\texttt{-This is the tallest building in the district. You can get a nice view at the top.\\
-I see. Enjoy your tea.}

I stand, and begin my ascent, leaving the tea untouched.

\begin{center}
    $\infty$
\end{center}

It began 28 minutes and 41 seconds after the completion of my ascension. Sundown. My sidearm had returned to its holster, and as the sky turned lavender, I study the interlocking patterns of the tower, by far the most intricate of the city’s architecture, despite the scars that time had left on its surface. The lead architects of the city made sure of that, for the tower was their abode. Missing panels, lost to gravity and wind, interrupted spiralling blocks that sought to reach perfection, and I am reminded of an oak on Terra, its centre hollowed out by rain and fungal decay.

Laughter echoes through the silence. My reverie is broken by the sight of a child running down the street, laughing as she chases down her older brother. An old man steps out of a building, holding something that resembles bread, cursing as the children run past him, while more shades fill the streets. Each hold a thermal signature analogous to a standard Terran; however, my sensors detect no variation in heat across the body of each entity. At least, not until they interact.

A few streets down, a couple stand two steps from the sidewalk, staring into each other’s eyes and exchanging sweet nothings. One of them whispers something under their breath, and their partner lets out a trilling laughter. They press their heads together before they meet their partner’s warmth through interlocking lips.

Heat, like a synaptic connection come to life, flares between two phantoms. 

Thousands of these connections explode around me, coming from friendly greetings to tearful goodbyes, like neural activity mapped onto the scale of an entire district. The city spanned hundreds of such districts, designed by the architects with the intention of both structural and functional modularity, where interpersonal conversations abstracted into inter-district interactions. Lines of heat crawled across the network like flaming webs of gold.

Memories and thoughts converge into sentience. It gave birth to an awareness, and it did not take long for that awareness to notice an intruder.

Wind brushes the side of my cheek with the lightness of a child's touch. A hint of petrichor hangs in the air, but the sky is clear; my sensors fail to pick up the usual signs of a coming storm. Nothing but the sense of something pressing against the fabric of the world gave away the City’s attention on me, like a thumb resting on the string of a guitar. 

I consider the package on my back, but there is no hostility to its touch. I am a novelty to the City. It wants something it lost - people. The phantoms on the streets are the dreams of a ghost city, yearning to be filled with everyday cries of joy and sorrow. 

I record as much as I am able, yet I am increasingly certain the City will not serve our purposes. It is a child. I will not allow it. Despite this, I stay. Perhaps there is something I can give.

As night falls, I slide down the trunk of a tree and onto the streets. Then, I run. Past dining lovers and drunken friends, who glance or give out a whoop in my direction, I sprint across the City – I dash down streets and zip across rooftops when I am able, crossing districts in a matter of hours. Shouts and conversations proliferate in the air, seasoned with a collection of perfume and cigarette smoke. Who knew that night is so alive? As I run, the City follows, and the tower watches above all.

Eventually, the clothing of the shades around me become more luxurious, and my behaviour attracts the watch. They give warnings then give chase, which I oblige by leaping across rooftops, much to the annoyance of nearby shades.

By the time I reach the field at the bottom of the tower, I am alone, save for the City’s attention. Synaptic flares have spread like wildfire across the districts, for it no longer played the same nights over and over again, but was finally able to remember a new one. Yet no flames burn within the tower -- it stood as a silhouette against a backdrop of stars. Perhaps the City does not remember them, for they lived so far apart from the rest of the living. Did the lead architects, looking down from high up in their tower, in the centre of the city, know how far they truly were?

Morning came. The shades return to their slumber, and the City goes to sleep, satisfied. I have given it all I could. 

I return to the teashop, but the old man is no longer there. The kettle sits empty and cold. I adjust the package on my back, and continue on my journey.

\begin{center}
    \texttt{End of log}
\end{center}
\text{ }