\noindent The Kingdom of Lucis was absolutely fucked. The Imperials had taken over the castle, and their influence had become apparent even in the furthest reaches of the land. Even in Cleigne, the soldiers had laid chaos to their once peaceful life.

The monsters at night started showing up in the day. Or maybe they just stopped disappearing at night. Who knew? Thankfully, L'eive didn’t have to deal with the direct aftermath of this apocalypse. His parents’ farm was far enough away from anyone important to attract attention from the Imperial soldiers, and the monsters didn’t really care about them if they stayed around the farm.
 
And L'eive was lucky to not suffer from solitude either. Not when his best friend lived with him.

Dielën was always there for him, with him. And he was everything he could ask for in a companion. Dark navy feathers covered his body, and he was dark as midnight except for his beak which was bright orange. He was almost 5 years old now, and he had grown to tower over L'eive, standing at an impressive six feet. His neck was long and graceful, making for a surprisingly sturdy handhold when going on rides. L'eive hadn’t had the heart to put a rein on Dielën yet. He deemed he was still too young.

But what L’eive loved the most about his pet chocobo was his soul. He had eyes of hazel, and L'eive could always tell how they brightened when he brought him greens to feast on, or how they seemed to follow along his pacing late at night at the stables as L'eive ranted about something or the other. Or how they held in them an immense and inexplicable understanding of the bond between them.

Dielën was the best flightless bird in all of Lucis, as far as L'eive was concerned.

He still remembered the day he had hatched. It was a lovely spring day, and the blue egg had cracked first. Slowly it had grown, growing larger and larger till it covered the circumference, and then - pop! A black mass of feathers and indescribably adorableness had entered his vision. 

Their vision. Eveilün had still been around back then - her family still had a farm in Cleigne.

L'eive shook his head, coming back to the present, to the night under the stars, waddled up in the comfy hug of a chocobo.

\begin{center}
    ***
\end{center}

\noindent They went on their usual morning ride the next day, with Dielën trotting over the plains, avoiding all the monsters by experience. They never ventured out too far, at most making it to the lake and stopping for Dielën to rehydrate while L'eive stretched away his lethargy.

But something about that morning made him nostalgic.

“Drink up, buddy,” L'eive said to Dielën, patting his back. He laughed, “I remember when you had just hatched, you wouldn’t drink or eat anything that wasn’t from Eveilün.”

Dielën only flicked his eyes to him and gave a soft squawk. He did not stop drinking from the lake. L'eive smiled. “I miss those days, you know?”

Dielën lifted his head and gave L'eive a comforting nudge with his still wet beak.

“Of course you know.”

Dielën dropped his beak back into the lake only to bring it out again with speed, splashing the cool, refreshing water all over L'eive.

“Hey - “ But Dielën was already running across the field, back towards their farm, squawking in what could only be characterised as mocking glee.

“Come back here, you little pecker!”

L'eive chased after him, even though he knew he wouldn’t catch up. But at least the pain from his past was forgotten.

\begin{center}
    ***
\end{center}

\noindent Dielën had a way of expressing himself that put many humans to shame. He had a honk for when he was excited about something, usually accompanied by that ridiculous dance he’d picked up from a travelling flock of Chocobos. It was hardly a dance - all he would do was spin around flapping his wings without any rhyme or rhythm. 

He did it everytime L'eive got him a special, tasty Green. He did it sometimes when it rained. He didn’t do it at all when his legs couldn’t move and pain wracked his fragile, majestic body.

On days like those, his honk was replaced by an almost silent whimper, and the moisture around his eyes was from clouds within rather than the ones above. It happened at least once a month, and it was L'eive’s understanding that it was normal and healthy. 

Still, he didn’t like seeing his best friend in pain. When he was younger, his uncle had explained to him that Dielën went through this ordeal as a trial from Bahamut himself. The astral didn’t want Chocobos to be so happy all the time that they forgot about others’ suffering. It made them grounded and flightless.

A silly folktale to shield L'eive from some complicated avian biology. But L'eive still remembered it, and he made it a point to be by Dielën’s side to remind him that he wasn’t alone.

Sometimes - most times - L'eive would hold his own shoulders with his palms and flail around, spinning and stomping his feet. Dielën squawked at him every time - whether to get him to stop, or keep going, L'eive didn’t know.

\begin{center}
    ***
\end{center}

\noindent In the fifteen years in which Lucis cowered before the darkness of the Imperials, L'eive and Dielën got up to quite a few adventures. Along the way, they earned scratches and wrinkles and scars that didn’t always heal. 

L'eive’s parents had been lost when he was twelve, and his uncle was gone soon after. The farm and its responsibilities fell on their shoulders, and they carried it together.

For so long, it was just the two of them, in the wet plains of Cleigne, toiling and working and laughing and dancing. Until one day, it wasn’t.

Lucis had finally been liberated after the Prince had awoken from his slumber. A Regis sat on the throne once more, and the evil in the sky and the ground disappeared overnight.

Lady Lunafreya and the Prince - King now - had a lavish wedding and celebrations reached even the remotest parts of Lucis. Tenebrae and Lucis were allies once again. The darkness was finally gone.  The day was bright and birds chirped without fear of being hunted. 

L'eive should have been happy, but he felt a distinct void in his chest. Usually he would have just sought out Dielën and cuddled with him a little bit, but the bird was woefully missing. He sat there on the front porch of his old house, looking into the horizon, trying to figure out what he would do next. 

But he heard that familiar honk of happiness and a natural smile came over his features. He got up from his chair and walked around the side of the building to the patch of Greens behind his house. It had been there since before he was born, and it was Dielën’s favourite place in the whole world. His enthusiastic honking made it very clear.

As he rounded the corner and saw Dielën’s midnight feathers ruffling in the breeze, he immediately noticed the body hugging his best friend. Dielën squawked once more, calling him closer.

But L'eive stood still, his legs unwilling to move. Eveilün was there, cuddling into Dielën’s side, scratching that spot under his beak and laughing and talking to the bird. She slowly turned her head his way and noticed him. Despite the longer nose and laugh lines around her mouth, she still looked as he remembered her. That same mirth in her eyes, and that same gleam in her smile.

She beckoned him over wordlessly, and he floated towards her.

She flashed him a dazzling smile, and it transported him back to twenty years ago, in that same path of Greens. To a moment when his heart was full.

To the moment of them kneeling into the dirt, holding between their tiny hands a freshly hatched egg and little ball of midnight.