\noindent The full moon slid across the night sky as the League of Femmes Fatales gathered for their centennial meeting. Lilith drummed her fingers on the marble table, eyeing the oversized clock that hung above an even bigger pair of double doors that connected Calypso’s island to the mortal plane. The other ladies busied themselves with conversation, but she caught Medusa, her right-hand woman and the face of tranquillity, sneaking a glance at the time herself. Those two were late. Again. Eve was going to be soo mad. The Mother of Humanity would say something along the lines of “the importance of work-life balance” and refuse to help with her hair the next morning. The feeling of impending doom looked her in the eyes and gave a little giggle. Lilith shivered.

The doors creaked open with the energy of a slumbering snail. Lilith glared at the pale goth who squeezed through the gap and hopped towards her seat, crimson dress shimmering at the hems. A fox followed suit, who strutted around the circular table as her fur melted into a silken robe, and the \textit{huli jing}, in her human form, took her place at the table with the regality of an empress. The room quieted.

“Finally, we can start,” said Medusa. “What held you up this time, Carmilla?”

The goth batted her eyes. “You’ve got really pretty eyes, Dusa. Are those new eyeliners?”

“Answer the question, honey. But yes, they’re from Egypt. Cleopatra was very generous. The men never seem to notice though.”

“Why do you never ask Daji? I sat down first this time!”

“I’m an empress,” said the fox spirit. “Being late comes with the title. You have no excuses.”

“It’s not my fault you set the meeting up so early!”

Lilith cleared her throat. “As has been said before, this is the latest we can push the meeting before half our members get too tired to function. This is a very reasonable time.”

The Skogsrå raised her hand. “I’m already feeling tired.”

“Try out instant coffee. Best invention Adam’s progeny came up with. My wife hates it though. Anyway, enough sidetracking. We need to get to the point. How is our progress towards world domination?”

“Truly horrible,” said the Skogsrå, “Our stocks are so low nobody even wants to blow our backs out.”

“But, honey, you don’t have one.”

Carmilla leapt up from her seat. “It’s going great! There was this book series that came out at the start of the century that was realllyyy popular. Then it got turned into a movie franchise and got even bigger! People have churned out so much fanfiction since then I couldn’t keep up with all of it. They got a lot of things wrong about us vampires, but change with the times I guess. At least we were hot in that one. It’s progress!”

A furry paw went up. Wolf-Alice. “Speaking of fanfiction, that same franchise gave our men a strong foothold in this thing called the Omegaverse. It wasn’t entirely to our benefit.”

Lilith nodded. “Good work, both of you. How about yourself, Daji?”

“The internet is a truly wonderful thing. Back in the Shang dynasty, my then-husband King Zhou had to come up with all sorts of entertainment to indulge ourselves in, yet nowadays, all that needs to be done is the click of a button. Have you heard of video games, my esteemed chairwoman? They have a powerful influence on the young, and we are rather popular in some spheres. Also, there is another aspect of the internet worthy of exploit. Our porn makes so much silver, even the top courtesans of old would grow envious. Their indulgence shall make us queens.”

“Okay…Good job, Daji? Anyone else?”

The siren beside Carmilla rubbed her chin in thought. “It’s not going so well for us either, but perhaps our strategy of luring seamen to their deaths is an outdated one. I would like to hear some suggestions.”

Carmilla almost jumped onto the table. “Oh! Me me me! You live out in the sea, so you must not get a lot of internet. Listen to this.” The vampire tapped on her phone a few times, then turned the speaker towards them.

\begin{center}
    ***
\end{center}

\noindent ``\textit{…belong with me$\sim$''} 

Silence fell around the table. Not a few faces had tears in their eyes. The Skogsrå wept. 

“That was…so relatable…” said the Skogsrå, and started bawling again. Medusa handed the nymph some napkins. 

The siren rubbed her eyes. “What was that?”

“Taylor Swift’s \textit{You Belong With Me}.”

“She is a muse. What genius…”

“You and your sisters got good voices right? Study the trends, change up your style, or even start a band! You don’t need fanfiction or whatever Daji is doing. You girls can be superstars!”

The siren reached forward and took the vampire’s hand. “Thank you. You are the greatest vampire ever known to mortalkind. How ever can I repay you?”

Carmilla reached down, a picture of benevolence. “I ask for nothing but this. Join my fanfiction club. Every Tuesday at my place.”

“It shall be done.”

The sight filled Lilith with warmth. “Great job, Carmilla. Is there anything else we need to discuss?”

“One last thing,” said Medusa, “It has come to my attention that this council does not fully represent the femmes fatales across the globe. It is time to expand our league. What better time than the 21st century?”

It was true. This council was small, and much of their knowledge was dated. If not for Carmilla, the siren would have continued singing to an empty sea, with no one to hear her songs. How many opportunities for growth – both personal and for their shared goal of world domination – have they missed in the past century? 

“We shall vote on this motion. Any objections to this proposition?”

Not a single hand or paw went up. “All in favour then?” Every hand shot up, and paws punched the air. Lilith grinned.

“Motion passed.”

Cheers and roars filled the room, but Medusa held up her hand, and the room quieted. 

“Before this meeting ends, there is something I wish to say. We are busy women, and seldom get the chance to meet each other in the span of a century. The only reason we all came together is because of our chairwoman. Calypso!”

Plates and glasses floated down from above, and bottles popped open, filling the glasses set before them. Calypso herself burst into the room, carrying a great cake no doubt filled with nectar, and her invisible servants followed in her wake with trays of ambrosia. Medusa turned towards Lilith, who fixed her with eyes that turned men to stone, gemstones that the very ocean once sought after, and raised her glass.

“To the first woman! The one who did not yield to Adam! Tonight, we feast!”

Lilith turned to the great clock on the wall, and sighed. Eve was going to chew her ears off.