\noindent A small, fluffy pair of 20-sided dice bounced up and down from the rear-view mirror, as Arantius’ three decade-old jeep dashed through the highway.

His mind entered a deep state of focus whilst driving. Almost becoming one with the car, he barely even had to move his well-trained eyes whilst swiftly overtaking others on the road. He looked out to the blazing sun facing west, pondering on the unknown realms of arcane.

The radio suddenly went quiet, and amidst all the brief static, thunder roared from the panel.

\textit{“Thou art now listening to…”} a voice announced, followed by the sound of a fireball being cast, \textit{“102.3, The Real Wizards FM!”}

“What!?” An out of tune note played from the passenger seat, where Merrylin the bard sat adjusting his guitar. “Oh hell no…” He reached out for the controls on the panel.

“Do not dare change stations!” Arantius warned him.

“This is garbage, Archie!” The bard curled his fingers and shook his hands in frustration. “How can you be so old and have not developed a good taste in music!?”

“Silence!” his deep voice echoed. “This is what the best of the best listen to.”

As the host’s overenthusiastic announcement came to an end, a slow mediaeval song began to play.

Merrylin glanced back and forth between the radio and the wizard. “Were you told that by a deaf person!?” he whined, quickly grasping the rotating radio button. “I’ll show you some real music-”

“No you don’t!” Arantius began slapping the bard and pushing him away as he shifted stations.

\textit{“On other news, the princess has once again been turned into a frog by-”} The newsman was interrupted as the wizard changed back to his favourite station.

“The driver’s word is the only one that matters when it comes to the radio.” He raised his chin and shook his index finger.

“Yeah, sure man, whatever.” Merrylin leaned back on the passenger seat, going back to tuning his guitar. “Maybe listening to this shit is what’s keeping all the witches away.”

Arantius growled, but figured giving his friend the attention he craved would simply make him angrier. He rolled his eyes and sighed, shifting his focus back on the road.

After a few turns leaving the highway, their jeep was forced to halt beyond the sight of a red light. Aiming for the first exit to the left, the wizard stopped his car behind a green van, covered with goblins’ symbols and scriptures.

Merrylin raised his eyes to the road. “Not this again! Don’t tell me we’ll end up stuck behind those idiots.”

“Never judge a book by its cover,” Arantius reminded him as the traffic light turned green. “In this world, all creatures opt for concealing their true intentions.”

“But they ain’t moving! The light’s green!” He pointed at the van. “How the hell did they get a carriage licence?”

“It must be a mistake on their part, I’m sure they’ll quickly-”

“MOVE, IDIOT!” Merrylin shouted, pushing Arantius back to press the horn in the steering wheel.

“Enough, you-” The wizard fought back, though his attempts to prevent the bard from honking proved to be fruitless.

It wasn’t until the van’s driver door opened that their childish fisticuffs ceased. A green, short creature walked out into the road, shaking his fist and swearing at the two.

Both of them fell back on their seats for a moment. Arantius rubbed his forehead in frustration while Merrylin tried to make out what the goblin was saying. Seeing all the creature did was to keep cursing and moving in, the bard was quick to respond.

“DID YOU NOT YOU HEAR ME, YOU FAILED GREEN ABERRATION? GET OFF THE FUCKING ROAD, BEFORE I PAINT THE ASPHALT GREEN WITH YOUR FACE!”

Baffled, the goblin turned to his van and opened the back doors.

“Oh no…” Both the wizard and the bard’s eyes widened.

As if a portal had opened inside that tiny van, a green swarm of gremlins armed to the teeth came rushing out. With knives, spears and even flails, the goblins charged at the jeep, ready to take both it and the people within it apart.

Seeing the situation get dire, Arantius wasted no time changing to reverse gear and fully pushing the gas to perform a tactical J-turn. He flipped the car in the other direction whilst speeding, and flew away from the horde.

He couldn’t prevent one or two of their pursuers from holding onto the car. But driving at almost 240 kilometres per hour with the assistance of his magically-enhanced engine would ensure they’d fly off before trying anything funny.

“Hahah! Nice work, Archie!” Merrylin laughed as he slammed his guitar into a goblin who’d made the foolish decision to stick his head close to his window. A few notes played as the creature’s skull was crushed by the mahogany instrument.

“This is why you should always keep your driver content!” the wizard laughed, launching the last few goblins off the car as he reached over 300 kilometres an hour.

As an inverse testament of its appearance, the jeep’s engine roared, blitzing the vehicle through the streets. The party’s joy was a short-lived one, however. From the rear view window, Arantius spotted the hybrid species which combined the brilliance of a human with the physique of a horse - a centaur.

“Pull over!” the centaur screamed at the top of his lungs.

The wizard sighed, but complied.

“Whaat?” Merrylin’s wide eyes turned to his companion as he slowed down the car. “Are you kidding me? We can’t afford another one!”

“Give me my staff, Merry,” Arantius said calmly, before bringing the vehicle to a halt.

The quadruped trotted around the car, moving closer to the driver’s window. “Do you know why I pulled you over-” His voice was interrupted by the wizard’s furious chant.

“DISCIDIUM EXTREMUM!” The words thundered out of his throat, resonating into the crystal in his staff’s edge. In a mere instant, it built up an incredulous amount of magical power, which was immediately channelled into the poor centaur beyond them.

A blinding light engulfed their surroundings for a few seconds. When the dust had settled, Arantius and Merrylin both looked out to face the product of their defiance. Standing on the ground just beside the car, a clueless man looked around to shriek in horror as his eyes came across a body which used to be his, now a horse on its own.

Merrylin’s jaw almost went loose. The man screamed in sheer desperation, but before anyone could think of anything to do next, Arantius pushed the gas pedal and left the scene as fast as they came in.

“What did you do to him?” The bard slowly turned at the driver.

“Let’s focus on the road, yeah?” The wizard broke his accent for the first time.

A crystal ball encased within the cupholder of the driver’s seat suddenly began glowing a teal blue tone.

“Someone’s calling ya, Archie.”

“I’ve got this.” He grasped his fingers around the sphere, “Shit-” and dropped it on the floor.

“BAHAHAHA!”

“SILENCE!” Arantius shouted. “Ugh, we must acquire another one if we’re to access myquest.co again.”

“Let’s just go old fashioned.” Merrylin’s eyes followed a sign on the side of the road. “There! We’ve got a tavern over there, I’m sure someone’s got something for us.”

The wizard sighed, making the turn. “So be it.”

The jeep was stationed on the unpaved parking lot in front of the tavern. A crowd of bystanders stopped to watch as the two of them walked out, exchanging caustic glances with the local populace.

Halting their step by the ‘NO WEAPONS’ sign at the front entrance, Arantius handed his staff to Merrylin.  “Leave it in the back seat,” he ordered as he walked in.

“Psh. Fine.”

The bard returned to the car, carelessly opening its back door to allow a skeleton leaning onto it to fall down and shatter on the ground.

“FUCK! BOB, NO!” He curled his fingers, kneeling on the ground and staring in anguish at the bones sprawled all over the soil.

Disregarding his friends’ cries of misery, Arantius continued his search inside for a quest which could pay for a new crystal ball.

‘I hope it wasn’t that witch I met the other day calling,’ He thought to himself, bumping into a lady with a comically large exclamation mark floating above her head.

“I must know how to do this-” He looked up to the floating object.

“Hello, traveller,” she started. “Have you ever heard of the tale-”

“I don’t care!” Merrylin shouted as he walked into the tavern. “How much is in it for us?”

The woman rolled her eyes. “Five hundred gold, including taxes.”

“Archie, that’s a shit ton of money…” the bard uttered in the wizard’s ear.

“I know.,” he uttered back, and turned to the lady. “What shall we do?”

“A bunch of crooks took over the enclosure where a railway crosses the closest river we got. It’s bad for business and makes the cost of everything here expensive. Wipe them out.”

“You got it, ma’am.” Merrylin immediately turned 180 degrees and left.

“Have our reward ready,” Arantius instructed, soon following his friend.

Walking outside with determined looks, they gazed up to the setting sun. Nodding and keeping a stiff upper lip to all the ones around them, they got the message across that they would get the job done.

“The enclosure is five kilometres uphill, Merrylin,” the wizard said. “Start the car.”

The bard’s expression fell. “About that. We’ve got a flat tire.”
