\noindent Specimen 18. A large arthropod-like creature, twenty metres in length and two and a half metres in width. It raised several hundred pairs of clawed appendages, and guttural screeching filled the air. A single nod and the restraints were thrown over the brute, cutting off its war cry as it flailed in vain on the forest floor. 

“Excellent work, men,” the scientist called out, taking meticulous notes on the creature’s physiology. Chances were low that it would survive the journey back, so a detailed record of the creature’s appearance and behaviour was integral. 

“Dr Kirkland.” 

Clearly, not everyone on the team recognised his dedication to scientific pursuit. 

Rolling his eyes, Dr Arthur Kirkland continued his note-taking. “Yes, Mr Jones?”  

Jones immediately launched into his latest delusion. “There’s something underground, I just know it. I’ve been hearing these noises-” 

“Ah, yes.” Clicking his pen shut and lowering his clipboard, Arthur offered his most condescending smile. “I’m familiar with this Hollow Earth Theory of yours. But you see, this is not Earth. Humanity’s new home will have no place for these inane theories.” 

Humanity’s new home. Underfoot, black grass formed an organic cushion, crunching slightly as Jones shifted his position. Above them, violet foliage hung from slender branches of lofty trees, occasionally scattering a purple leaf or azure blossom with every whisper of the breeze. Beyond the trees, hazy white clouds did little to cool down the warmth of two suns in a blushing sky. The grey smog of despair and paranoia they’d called home seemed a hazy memory in this utopia, and Arthur intended to keep it that way. 

A flurry of activity by the truck broke his rapture, and he tucked his clipboard to his chest with a small sneer. “Run along, Jones. You wouldn’t want to miss our chef’s latest creations. I hear he’s rehydrated a new type of pasta!” Not waiting for a response, he marched away, eager to hide in his makeshift study where he would feast like a king on his own rations of equally miserable slop. Lead scientist he may be, but all suffered equally through pioneer gruel. 

The study was little more than a small table around the corner, hidden from view of the crewmates at the canteen. After Jones had hurried to join the throng, they had set out two large folding tables and surrounded them with metal chairs to languish on while congratulating themselves and stuffing food into their faces. Unimpressed by their display, Arthur sat delicately at his own table and began to eat, pretending to be unaware of the loud conversation a few metres away. 

“Rejected by Dr S again, Alfie?” someone piped up, and Arthur rolled his eyes. 

Jones had managed to slip up before they had even left Earth’s orbit, and still remained the butt of every joke. It wouldn’t be so bad if the young man had enough wit for a riposte, but instead he would always stand there, red-faced and tongue-tied. 

“Leave the boy alone,” a stern tone chimed in, and Arthur winced slightly. Beilschmidt was a very serious man, and his defences were never kind. “It’s not his fault he believes in such silly stories.” 

Scattered jeering met his words, and Arthur allowed himself a dignified snort before continuing his food. It was uncivilised to eavesdrop, but who didn’t like a show with a good meal? Or, looking at the congealed rations, maybe just any meal at all. Scraping the plastic fork against the paper bowl, he managed to scoop out the remains and tip them into his mouth. Now to dispose of the kitchenware... After a few moments of inspecting his surroundings, he walked over to an inconspicuous bush and gently pushed the bowl and fork through its foliage until they were barely visible. They were adventurers, after all, and the first rule of exploration: leave no trace. 

Behind him, there was a loud slapping of skin. “Damn bugs!” Bonnefoy exclaimed, to Arthur’s amusement. The Frenchman had been miserable from the start of the journey, and if he weren’t so entertaining when upset, Arthur would have long been sick of his antics. “I hate this planet!” he continued, clearly preparing to launch into another tirade, famous for being so irritating to listen to that it raised team morale. 

“I’ll never understand why you came here, Francis,” Beilschmidt’s weary voice cut him off. 

A haughty sniff. “For the money. When we return, I plan to kick back with the finest wine the institution can afford.” 

Arthur could get behind that, and so could their colleagues. Mutters of agreement and “I’ll drink to that!” accompanied the scraping of disposable cutlery on bowls, and Arthur took the chance to make himself scarce. Anyway, he brought up a good point. Insect populations had been all but decimated back home, but they still knew very little about the minifauna populations. Now wary, he glanced back at the bush, shaking his hands slightly. Who knew what kinds of alien ticks and parasites could be lurking in this habitat? The scientist shook his head. It was time to find a new location. The truck was easily reloaded, and the crew were eager to explore new horizons. Before the closest sun set, they had already driven away leaving no clue of their presence other than trampled tyre tracks, lingering petrol fumes, and scattered piles of disposable goods poorly concealed among the trampled plants. 

Location 13. Just beyond the boundaries of the vast alien forest, a carbon-black meadow stretched out to distant horizons, accompanied by a great lake mirroring the now darkening reddish sky. The crew stifled yawns as they set about observing living conditions: Arthur ran a tight ship, and insisted on air conditions, water quality, and soil nutrient levels being recorded before anyone could finally return to their bunks for the night. He, of course, sat wrapped in a throw while watching his crewmates struggle with their little measuring tools and write with spasming fingers, and felt just as satisfied as any of the shivering men when heading off to bed. 

Arthur’s dreams that night were strange. A rumbling noise reverberated in his ears, growing louder as a giant alien tick reared onto its hind legs and bared venomous fangs. Jones popped into view, whispering, \textit{“There’s something underground, I just know it,”} until the tick fell forward and burrowed into the soil. A giant hand slapped down on where it had been, and Bonnefoy shouted, \textit{“Damn bugs!”} as Arthur was thrown off his feet from the force. Instead of hitting the ground, he continued falling, into darkness as the roar grew until- 

Awake now, he forced himself to breathe evenly. It was a few moments before he could manage to sit up in his bunk and wipe the cold sweat off his forehead with his damp pyjama sleeve. Even now, he seemed to hear the noise, fading into the distance along with the dream itself. A few bunks down, Williams snored loudly, and Arthur shook his head. He’d let the others weaken his resolve, and that had manifested as a paranoid dream. Flipping his pillow over, he laid back down and let himself drift off again. He’d need sufficient rest for the next day’s work. 

Unaware of any strange events in the previous night, the rest of the crew awoke with surprising energy to begin the day. The threat of rations potentially running out had hung over their heads, and Arthur was amused to see the crew’s excitement at a source of both potable water and potential food. All the fauna they had encountered had been captured for science, but the contract hadn’t said anything about aquatic creatures, so he said nothing as they took advantage of this loophole. The native fish were strange with their dozens of fins and moss-covered hides, but arguably not more unappetising than monkfish or hake, or even the lab-grown protein slabs that Arthur had grown up on in his upper-middle-lower-upper-upper-lower-upper-middle class family. Still, Vargas the chef did not have the same allowances; faced with Beilschmidt and Williams clutching massive nets loaded with wriggling finned alien fish, he looked offended at the poor quality of meat chosen for him to work with. An artisan could only work with the very best, so more than a few cadavers were tossed back into the lake after only having a few slices of meat removed for consumption. 

Arthur was detached while watching the crimson blood streaks spread in the golden water. It was wasteful, but there would always be more. In fact, judging by the now frothing surface of the water, the local wildlife seemed to appreciate their input. The men were enjoying the scene too, dangling corpses over the water to encourage the aquatic carnivores to jump for their food. The fun was cut short when Bonnefoy – \textit{of course} – hollered, clutching a bleeding stump where his arm had been. As the closest they had to a medical professional, Arthur had to leap into action, ushering his traumatised crewmate into the truck for treatment. 

It took some time, but eventually he’d managed to stem the blood flow. Bonnefoy had, for once, remained stoic during treatment, to Arthur’s relief. He was ready to remonstrate the Frenchman for his carelessness, but Bonnefoy gripped his arm with his remaining hand. 

“Will I be okay?” he asked in a low tone. 

Arthur hesitated, eyeing the bandages. Bonnefoy was pale, but unusually calm as he waited for a response. Maybe it was the absence of his usual melodramatic moaning that unsettled the scientist, but a twinge of compassion finally won out, and he gingerly sat on the edge of his crewmate’s bunk. 

“This won’t last as long as you think,” he said sincerely. “Just rest for now, and it’ll all be over soon.” 

Reassured, Bonnefoy remained recuperating in his bunk as Arthur exited the truck again. He considered giving a speech to his crewmates on the dangers of carelessness, but his sense won out. When he re-emerged from treating the invalid, Jones was busy skipping rocks on the lake as various aquatic beasts snapped at the ripples on the water surface. He doubted that any of them would take such a warning seriously, if their colleague being injured seemed to worry them so little. 

Perhaps the decrease in morale was tempered by the absence of Bonnefoy’s regular complaints. In the early afternoon, Arthur confirmed his patient’s worsening condition, and was almost relieved when Williams suggested an excursion back into the forest. Perhaps Bonnefoy would be gone by the time they returned, and at least Vargas would no longer complain about not having access to meat. The thought was revolting, but he had to be detached, rational, objective about their survival. The effort of staying upright made his head spin, and he could barely follow his crewmates as they hacked a path through the undergrowth. Why were they doing so, anyway? Surely there were clearer paths. Maybe it just seemed like the right thing for explorers to do. 

“Over there!” 

Beilschmidt’s bark drew his attention, but he only turned his head in time to see a dark blur escaping. The men gave chase, Arthur stumbling behind the others. His ears rang with adrenaline, but beneath the high-pitched whistling stirred something low, something deep. Ignoring it, he sped up, reaching the group as Jones held out a net gun, sending the strange creature sprawling to the ground, thrashing and screaming. For a while, the men all stood in silence, observing the alien as it howled. Arthur slowly stepped forward, regretting that he’d forgotten his clipboard. The creature descended into hissing as he approached, glaring up at him with wide amber eyes set in a curved reptilian face. But – most importantly – it sat on two legs, with two hand-like appendages struggling to lift the rope. It was humanoid. 

“We’re not here to hurt you,” he offered, holding out a hand palm-up in a gesture of friendliness. He’d read somewhere that it worked on cats. 

\textit{Liar}, shot into his head. \textit{You have hurt us enough}. 

It was as though the creature had spoken directly inside Arthur’s skull, and he shook his head. Obviously just more guilt manifesting. He needed to get a hold of himself. Standing up, he brushed off his legs, dimly aware of a growing noise in the background, like the crashing of waves on a beach. 

“Take it back to the truck, men,” he called over his shoulder. When there was no response, he turned around fully, his feet trudging on muddy ground. Muddy? Looking down confirmed what couldn’t possibly be true. What had been dry soil was now clay-like sludge, and his feet were sinking further with every step. 

\textit{Gone}, the voice in his head told him. \textit{And you will be too. }

A golden glint in the ground caught his eye, and he squelched over to it. A pair of glasses, slightly bent from when Jones had fallen asleep on them. If they were gone... 

He forced his way back to the creature, which was still and silently watching him. 

“Where are they?” he managed to ask. “What did you do?” 

No response, not even in his head. A trembling hand reached into his coat, pulling out a pistol. 

“I’ll kill you,” he choked out. 

Images flashed in his head – a pale corpse with rotting flesh still staring at the ceiling of his bunk, three carcasses screaming silently underwater as hungry creatures flayed them for food, a blinded cadaver preserved in boggy soil, eternally staring up at him reproachingly, \textit{“There’s something underground,”} – and he leaned forward and vomited. The alien watched steadily, and Arthur finally became aware of distant rumbling. It was coming closer, vibrating the soles of his boots, and if he weren’t so drained from guilt and regret, he would be flooded with terror. Instead, he was determined to not go down without a fight. Somehow, he managed to aim and squeeze the trigger, but the gunshot was drowned out by the ascending roar and the creature didn’t flinch as golden blood flowed from the wound between its eyes. The ground fell out from under him, and rows of teeth blocked out the sight before he could wonder why. 