\noindent Every year, spiders eat thousands of people. Don’t worry, you’re perfectly safe, spiders only eat a little bit of anyone, unless you’re unlucky, or they’ve eaten your luck. 

It’s best not to write about the spiders, as they will read it, but considering my circumstances… 

I have a few fellow researchers; there used to be more of us, but the spiders ate them. And they died.  

Virgil died a month ago. The spiders ate his sleep. It sounds wonderful at first, not having to sleep, but what the spiders ate was not his need to sleep, but his ability to do so. He died overdosed on sleeping pills, bloodshot eyes wide awake.  

Do not write the names of anyone alive while thinking of the spiders. It will call them. More than one quarrel has ended with all parties involved eaten by the spiders. It has been taboo for us to write the names of anyone alive ever since. 

Being eaten by spiders isn’t necessarily fatal. Someone whose name I forget had some of their memories eaten. Sometimes they would walk into a room and forget why they had, or forget to eat, until the hunger was overwhelming. At first, the rest of us didn’t think much of it, until we saw the spider on their head. I don’t remember what it looked like. 

There were some, I think foremost being Celia, who thought we could use the spiders to our benefit. She managed to get the spiders to eat her past and was scarily gleeful. Problems arose after she tried to have the spiders eat someone else’s bad feelings for her. She knows better now.  

That incident led to our other rule of “Don’t encourage spiders to eat someone else” Some spiders are harmless. I admit to sometimes feeding my inhibitions to the spiders. It’s cheaper than alcohol and doesn’t leave a hangover. Sometimes I regret what I do, however. 

Once you are aware of the spiders, you can influence them with their silk, in a process too complicated and gross to describe here. It is not precise, unless you spend a lot of time getting into the minds of the spiders. 

Now there are some breeds you can’t do this with, like the spiders that physically eat you. I forget our proper name for them. These spiders don’t make silk. They do lay eggs though.  

Phoebe had her fear eaten, and is surprisingly still alive. She does still have an instinct for self-preservation, but maybe the spiders will eat that too.  

You are unlikely to be eaten by most spiders, unless you know about them, but there are some exceptions. These result in so many deaths that they are anomalous and should not be counted. Spider George is one notable example. It tricked one of us into working for the spiders, feeding them our trust. The few of us left will never meet again.  

Then, having divided us, it started hunting each of us down. The spiders ate Julia’s health, and she withered away. They ate Danny’s weight. His tether broke and he floated into the cold sky. We don’t know what they did to Meryl, but one day, he just disappeared. The spiders ate Joel’s eyes. 

The few left of course have their suspicions that someone has turned, but there is no way of knowing who. The survivors have all gotten close to the spiders. 

There is a consolation though, we know the spiders will eat the traitor last. 