I woke up in a daze. I recognized that I was in my own bed, in my own bedroom, but there was something  in the air that felt wrong. Firstly, I noticed it was still dark out. I had been awoken unexpectedly. Secondly, I realized the reason for my rude awakening. There were hushed whispers and strange noises coming from the other side of my bedroom door. And thirdly, perhaps the most troublingly, the other side of the bed was empty, with no sign of Elizabeth in the room.

I slowly sat up, looking around for my girlfriend, while trying not to panic. There was probably a perfectly reasonable explanation for what was going on. But my heart paid no heed and continued to beat faster. I distinctly remembered El sleeping next to me the previous night, but her side of the bed was made, as if she hadn’t been there at all. 

Wide awake, I quickly got to my feet and rushed to the door. Pressing my ear up against it, I strained to pick up any sort of voice or word that I could recognize. 

“Clear,” someone said, in a high pitched voice. The voice was foreign and the tone sent chills down my spine. She - I assumed from the voice that the speaker was a she - continued talking, but I could only make out a few words. 

“- not here. … have escaped….alert them. ”

To say that I was incredibly confused would be an understatement. I could not wrap my head around the events going around me. It could have been that the cobwebs of sleep still fogged my mind. Before I could think of doing anything else, I felt a forceful push on my cheek as someone kicked open the door I had my face pressed up against. 

I fell backwards, landing painfully on my head. I saw a man dressed in a black suit enter my room, and the last thing I thought before my vision went dark was that I was probably dreaming.




When I came to, I realized that I was not dreaming. And the thing that gave it away was the massive, white walled room that I found myself in. I was sitting upright, clamped to a chair as if in an interrogation.

My eyes were still a bleary mess as they adjusted to the bright light in the room, but I could hear the sounds of boots on linoleum and the smell of disinfectant wafted up my nostrils prominently. My eyes resumed normal functioning in a few seconds and I took in my surroundings, noticing the size of the room and the bare walls that made it up.

I also noticed that I was alone. There wasn’t anyone else in the room apart from me. There probably wasn’t a speck of dust in the room either. Understandably confused and terrified, my heart beat skyrocketed as I tried to reason through the situation. 
But it didn’t make any sense. What would anyone want with a 22 year old college student? Why would anyone go to so much trouble to kidnap and detain me? I wasn’t rich or famous, and neither was anyone close to me. My mind spun from all the unanswered questions swirling inside. My heart was threatening to burst at how quickly it was beating. 

But suddenly I heard a voice speak up, seemingly emanating from the walls of the room.

“Calm down, Kath,” it said, and I recognized it almost instantly. It was El. “Just take a few deep breaths.”

I acted on the advice and tried to calm myself down. She did always have a calming effect on me. Ever since I’d met her two years ago. I felt my heart slow down as some much needed air entered my lungs. 

The fog of panic lifted from my brain, and I tried immediately to figure out how El was talking to me. Maybe they had captured her too?! My heart rate spiked again.

“I’m fine, Kath. I haven’t been kidnapped. I’m safe,” I heard her say, seemingly from nowhere and everywhere. It was an incredibly strange sensation, hearing her voice in such a bodiless manner. Almost as if she was talking to me in my mind. 

“You always were smart,” came the reply. My eyes widened.

Somehow, even though I had never experienced telepathic communication before, I felt an odd sense of safety and tranquility. Despite all the burning questions that popped into the forefront of my mind, despite the excitement I felt at witnessing a metaphysical phenomenon, despite everything going on around me, I felt incredibly calm.

“Okay, Kath. We need to get you out of there,” said Ghost-El. 

Get out of where? Where was I? 

“I’ll explain everything. Just do as I say. And trust me,” she said firmly. But I was able to catch that same feeling of care and love that I had come to associate with her. I trusted her completely.

“Close your eyes and focus on my voice. It will all be over soon.” 

I did just that. Her voice had an angelic quality to it, and I couldn’t help but be entranced. 

“Great, just continue staying calm. You’re doing great. Just one more minute, and -”

I suddenly felt a strong breeze around my body. A whooshing sound accompanied it, and I found myself clutching the handles of my chair instinctively.

Suddenly there was silence as the breeze ceased. I did not dare open my eyes. Was it over? Where was El?

Before I could go into another panic attack, I heard her speak.

“It’s over, Katherine. You can open your eyes now.”

The visceral quality of her voice that I had been experiencing up until now was suddenly and strikingly absent. It seemed to be coming from in front of me. Almost as if she was standing right -

I immediately opened my eyes. And there she was, looking at me with a smile on her face. I realized with a start that I was in a completely different place. My poor brain was struggling to make head or tail out of the situation and the recent change in location did not help one bit. I looked at El’s face a bit more closely. She looked tired. Bringing me to her must have drained her somehow.

There was a silence between us for a moment, but I broke it. 

“Are you okay?” I asked.

El only smiled and came closer to hug me.

I was relieved to hear that she was fine. But I was still incredibly confused.

“You’re probably wondering what just happened,” she said.

I nodded my head. My brain was hurting from trying to wrap my head around the night I had just lived through.

“Well, the short of it is that I’m a telepath. And I can teleport things,” she said casually, as if it wasn’t something that violated the laws of the universe.

Naturally, I was at a loss for words. But she continued.

“And the people that took you, momentarily,” she smiled at that word, “are a secret branch of MI5, tasked with dealing with and handling supernatural phenomena.”

She paused as a grim look crossed her face.

“And they have been after me ever since I was a baby.”

I couldn’t believe my ears. My mouth was still unresponsive as my brain failed to produce any impulse to say something. It just felt like too much. 

But the weird thing was, I believed what she was telling me. The whole situation was absurd, and I was desperate for any sort of explanation. And I trusted her completely.

There was a small moment of silence as I processed El’s words. This was easily the craziest thing that had ever happened to me. And it took a moment for my brain to catch up.

“So, you’re on the run from them?” I asked.

A dark look crossed her face as she nodded. “And now you are too.”

My eyes widened as it finally hit me. That the supernatural and extraordinary events - like telepathy, telekinesis, and teleportation, apparently - were all real. Everything that had happened to me in the past God-knew-how-many hours was all real. It was surreal.

In a single night, my perception of reality had changed in more ways than one. My girlfriend was a telekinetic, a secret government agency was after the both of us and I had just been rescued from said government agency via teleportation. 

To say it was surreal was an understatement. My whole world had turned upside down. But if there was anyone that I would want by my side as I left my normal, lacking-supernatural-events, boring life behind, it was El. 

And that made me accept the fact that I was leaving my normal, lacking-supernatural-events, boring life behind for good.
