%\hangindent = 0.7cm \begin{quote}
    \emph{$26^{th}$ January, 20XX}\\
    \emph{In the past three months, six children from the local county have disappeared under suspicious circumstances. After banging my head against the wall for the better part of a week, I have finally managed to identify a common thread – a middle school Biology teacher who goes by the name of Mr Edgars. I have his address at hand (it’s in the middle of nowhere), and I approach his place of residence with nothing but a sense of grim determination.}
%\end{quote}

It snowed in January, back when I first met him. The inspector snapped his diary shut as his partner climbed onto the passenger seat beside him, chilled air seeping inside before the man closed the door. 

“You got a lead. Where to?”

“Somewhere southwest, far out of town. Middle of nowhere.”

“Easy for scum to hide, I suppose. Hit it.”

“Seatbelt.”

“Right, right.”

The inspector drove out of the parking lot, wheels crunching on salt and snow. His partner handed him a cig, which he accepted. Wind howled and battered against the side of their vehicle.

His partner tapped on his phone. “Have you ever heard of the Trolley Problem? It’s pretty popular on the internet these days.”

“Sounds like something the kids would love.”

“It’s a thought experiment, actually.”

“Oh?”

“It goes like this. There’s a trolley barrelling down some railway tracks, and five innocents are tied to the rails. You’re standing next to a lever and if you pull it, you change the trolley’s path, but there’s a single innocent on that other path. Do you pull the lever?”

“Hm. I think I do. Absolutely.”

“That’d make you a murderer.”

“Our whole job is to make sure as many people as possible stay safe. That’s why we lock the dregs behind bars, and if worse comes to worst, you’ve got to get your hands dirty. That’s all I’m saying.”

“Well, let’s hope the worst never happens, eh?”

“Amen, brother. Amen.”

\centerline{***}

They arrived in the afternoon. The inspector locked the car behind him, and took a last, long pull from his cigarette before crushing it under his heel. Half-molten snow crunched beneath leather boots as the two approached the house, where droplets dripped from icicles on the eaves, and rolled down chilled stone bricks before freezing again on the window frames. Blank, dull windows watched the inspector climb up granite stairs to the porch then knock on the wooden doors, once, twice, three times. His partner looked up at the windows.

“Looks like no one’s home.”

“You think so? Mr Edgars! We’ve come to ask some questions!”

No reply came except for the rasping of wind on stone, and even snow stayed on their crooked branches, for there were no squirrels nor birds to disturb the silence.

Glancing at his partner, the inspector tried the door, and was surprised to find it unlocked. He hesitated for a moment before deciding that he cared little for the privacy of a likely criminal, and stepped foot into the bowels of the house. His partner followed without complaint.

Soft carpet embraced the grooves on his boots, wetting itself from the moisture, as the inspector stood in the middle of a corridor, empty barring a few drawers and one of those vintage grandfather clocks that sat on four legs. It squatted against a wall, a little off to the side, and its pendulum swung in a broken pattern, faster to one side than the other, like the rhythm of a heartbeat.

Two sets of stairs stretched on to his right. One rose to the floor above, while the other led to the cellar. As it was unlikely that anything incriminating would be hidden in the open, the inspector signalled for his partner to check the cellar as he climbed to the floor above.

Although the curtains were drawn, and windows shut, the air seemed to breathe and stick to his cheeks when the inspector climbed the creaking stairs. He reached the landing with a half-held breath and looked for the man’s study, which he discovered to be the room to the left, its door ajar. He pushed it all the way open, and stepped through.

A bookshelf waited in the corner, with a modest collection of textbooks and fiction placed meticulously on its shelves, and one had a chameleon on its cover, skin blending to its surroundings as it waited for its prey. The ordered shelves stood in stark contrast to the stacks of paper and folders leaning against one another on the desk, like a tower of pebbles threatening to collapse. He skimmed through the documents lying on the desk without touching them, but the drawn curtains blocked out most of the light, so he tapped on his phone and turned its screen on, then cursed.

When he scanned the content on the desk, he had dismissed what he thought were ordinary paperweights holding the sheets down for some semblance of order, as if there could be some method to the madness, but under the dull glow of his phone, the paperweights revealed themselves as six white rings surrounding a bit of solid brown, each unique in size and thickness.

Like parts of a tibia, cut from a child.

Before he could do anything else, a tremor reverberated through the house. Someone screamed. It came from the cellar. Then a door creaked open from the floor below, followed by a rapid pattering of footsteps. The inspector dared not breathe as he held onto the side of the desk. His partner was in trouble. He had to get to the cellar. He took off his wristwatch and wrapped it over his knuckles then crept down the stairs, one hand on the wall. The wall rose and fell under his fingers and felt strangely warm, like the breathing of a beast, as his heartbeat echoed in his skull, the planks groaning from under his feet until he reached the foot of the stairs. Chill air crawled into the house through open doors, revealing a black convertible parked next to theirs, and his eyes flickered towards the entrance to the cellar, left unclosed like the maw of a carnivore. Edgars was in the house, and his partner was in danger. He had to go into the cellar.

The beating of blood thundered within his brain, so he clenched his fingers, breathing shallow breaths, and made his descent. He turned on his torch, and the shadows from below retreated to the edges of the light as he pressed on, one foot before the other, each step resisting the primal instinct to run, and leave this place behind.

Then no more steps remained, just a corridor to the end. The inspector kept his pace, and the walls seemed to press closer, like the constrictions of an oesophagus. A muffled sound emanated from beneath the stones, mixed with a hint of liquid sloshing in a bowl, and then silence returned. When he reached the end, he found the cellar door open, obstructed by a wall of darkness, which the light of his torch chased back. He took a deep breath, then pushed through.

Warm air caressed his skin. Cabinets of wine and various spirits lined the walls, hidden behind a pane of dust-rimmed glass. Shadows prowled at the edge of the light, lying in wait for a moment of weakness. A pack of cigarettes lay abandoned on the floor. His partner’s favourite. The inspector turned on the spot, wristwatch clutched in one hand until he noticed a single wine bottle missing from its row, and the reflected silhouette of a man raising it above his head. 

The bottle smashed against the glass as the inspector ducked and spun, slamming his wristwatch across the bridge of a nose, and he felt a satisfying crunch. His light flew from his hand and skidded to a corner as the two men wrestled at the boundary, the shadows on the wall turning into beasts to rip their fellows apart. Blood chimed in his skull. Edgars was stronger, and bigger, but the man was not trained, and after a moment of struggle, let the inspector slip under his swing to use the momentum to throw him into the glass. As broken shards showered onto the larger man’s frame, the inspector locked the man’s wrists behind his back and clicked a pair of handcuffs in place. Jagged edges cut into flesh, and blood dripped onto the floorboards.

“Mr Edgars, you are under arrest for the senseless murder of six innocent children. You have the right to remain silent. Do not resist.”

The man sputtered behind bleeding lips. “Senseless? I am a hero. I’m the one who’s keeping it here.”

“Tell that to the bars of your prison cell. What did you do to my partner?”

“He was an idiot, and so are you. You should have stayed far away. What if you scared it off? Imagine if it had gone to more populated areas, like towns and cities. It’d be like a buffet before anyone figured out why, if they even do.”

“What are you talking about?”

“It’s the house, inspector. It’s like a chameleon, but far superior, far more resilient and far, far more intelligent, adapted to completely conceal itself from human senses. And it loves our flesh. It’s addicted to it. I tried to gather evidence but no one ever listens. This was the only way. You have to believe me. I didn’t want them to die, but the needs of the many outweigh the needs of the few. Sometimes you have to get your hands dirty.”

“What–”

A tremor shuddered through the earth, and flung the inspector backwards as he was adjusting the cuffs. Wine cabinets swayed, bottles clinking in their display. 

“It’s the house, inspector. The house is alive.”

The ground cracked open beneath the bloodstained glass next to Edgar’s feet, revealing too many rows of serrated teeth. The inspector watched as the man hung in the air for a heartbeat, shock flashing across the teacher's face, before it plunged into the acidic fumes below. The crack sealed shut before the first screams reached his ears, then he was alone. 

Blood hammered against the confines of his skull, yet the house did not devour him. He struggled to understand when he ascended the stairs, until he stepped out the front door and took one step onto frozen earth, bloody shards falling from his shirt like rose petals on snow, bringing crystal clarity. No one would believe him. No one can help him. The needs of the many outweigh the needs of the few. The beating of his heart aligned with the rhythm of the broken grandfather clock. There was only one thing to be done.

He became my favourite servant.
