Esmerelda groaned and rubbed her temples as the fairy-phone rang for the seventh time that afternoon.

“What now?“ she growled, yanking it off the hook.

The caller was unaffected by her tone. “You won’t believe it. It’s happened to Caelia and Grimhilde too!”

“Well, it would have to be all of us,” Esmerelda replied drily, looking longingly at her empty bottle of pixie-liquor. “Everyone at that damned dinner.”

“Carabosse’s going too far,” complained the speaker. “All this because her invitation was lost in the mail.”

“You mean you forgot to send it to her,” Esmerelda corrected. “But I’ll allow bygones to be bygones.”

There was a pause, before a weak excuse was attempted. “Well, I had to help Arugula wash her hair...”

“Enough! I don’t know why you never let that foolish girl ever get a haircut. Even I let that ash-covered thing visit the village barber once a month.”

“Only because you hope he’ll marry her so you don’t have to provide-“ but the argument was cut off by her slamming down the fairy-phone.

\emph{Damn Gothel!} She cursed, staring out of the window at the lush fields outside. Beyond them ran a sparkling stream where she knew that half-fish creature was frolicking. She’d appeared this morning, looking like a normal teenage girl from the waist-up and had made her own two daughters dreadfully insecure, but after that she was all fish. Not at all capable of completing any of the chores the other girl had done. Completely useless! All because Carabosse had thought she was being excluded from a dinner. Gothel should have known better after what had happened the last time this situation had taken place – wasn’t there still a princess in a nearby kingdom sleeping her life away?

The fairy-phone trilled once again, and she snatched it up.

“If you don’t stop bothering me, you elderberry-reeking old hag-”

But instead it was Caelia’s drawling voice. “Well, I am relieved to not be the only one out of sorts.”

“Caelia.” Esmerelda narrowed her eyes, putting two and two together. “So the fish-girl is yours.”

“You have the mer-princess?” Caelia’s relaxed drawl sharpened, and Esmerelda chuckled.

“You still haven’t scammed her out of her voice? You’re getting rusty, my aquatic friend.”

“And you still haven’t sold off your step-daughter’s hand in marriage, you twice-widowed old bat,” Caelia replied bluntly. “What do you want?”

“My step-daughter, of course.” Esmerelda leaned back and swiped a finger along the surface of the desk, wrinkling her nose at the fine layer of dust on her fingertip. “Your little princess just can’t get any chores done and of course my precious girls can’t be expected to live in filth.”

“I’m afraid I can’t help you there. I’m looking at a girl and a tiger on the shore beside me, and I’m sure if I get too close I’ll become calamari. I’m guessing she’s with that diplomat you invited.”

Esmerelda dimly remembered a red cloak and staff, and nodded. “That royal vizier. I remember he was giving Grimhilde advice. All that sorcery nonsense when they already have power.”

“And you have no magic or power,” Caelia replied blandly. “Do you know how to contact him?”

Ignoring the slight, Esmerelda sniffed. “I’ll have to ask Grimhilde. But she’s having her own problems. Gothel too.”

“Gothel deserves it!” Caelia snapped in disgust. “Complaining to me about some young thing with sunlight deficiency making her insecure. What do I care?”

Esmerelda snorted, and hung up.

Grimhilde was frazzled when she answered the fairy-phone. Esmerelda would have felt pity for her if she’d been capable of it.

“We have to undo this,” she whispered as soon as she answered. “I went to visit that brat and sell her a poisoned comb and she wasn’t there! There was some girl asking if I sell books! As if intelligence is more important than beauty!”

“There there,” Esmerelda responded soothingly. “I’m sure she didn’t mean it. Of course everyone is just as obsessed with appearances as you are.”

There was a sniffle, and Grimhilde replied in a teary voice, “Thank you, I’m just still really shaken up about it.”

Rolling her eyes, Esmerelda leaned back in her chair, admiring the collection of medals her daughters had won throughout the years. “And you know of course whose work this is?”

Grimhilde hesitated. “You?”

“Fool! Maybe if you actually had a brain under that pretty face of yours, you’d have been able to kill your step-daughter the first time!”

“Well, maybe if you had a pretty face, you wouldn’t have had two men leave you,” Grimhilde countered sulkily.

“They died, you skin-bleaching bimbo.” Esmerelda pinched the bridge of her nose and tried again. “You realise this is the work of Carabosse?”

“I did wonder why she wasn’t attending the last group dinner,” Grimhilde remarked. “So Gothel didn’t invite her?”

“And now we’re all suffering for it,” Esmerelda agreed grimly.

“Why do bad things always happen to good people?” Grimhilde began to wail, but Esmerelda cut her off.

“Of course, her spells all have a limit. We know everyone from the dinner so we can easily set things back on course. What remains is our response.”

“Carabosse’s going to learn that we’re not to be taken lightly,” Grimhilde agreed, finally on the same page. “But how?”

Esmerelda smiled deviously, looking down at the Royal Ball invitation on her desk. “Isn’t there a teenager in a death-like sleep out there? And don’t we all know a prince or other?”

“You mean\textendash“

“Yes. Carabosse will never see it coming.”
