On the 19th of July, the sun baked the earth, and I was setting down a whetted bucket onto the cracked earth. Like any other day, I was checking the moisture traps, and refilling the last day's usage. In the valley where I lived, there was little water, and what water there stubbornly remained in the air, to live out there, water was everything. As I was checking the water levels on the main storage tanks, I asked the house's computer 'What's the plan for today?' The screen responded, telling me of the 2 wet traps left, and that dinner would be at 6:30, noodles and broccoli, with some chicken floss. I had not eaten broccoli in a few months, not since the last nutri-shipment, and I remembered the packaging, little green trees. Then I remembered.

The sun was setting and the ground was wet under my feet. The faintest breeze passed by, shuffling the trees and setting off the windchimes of the house. I sat down, and watched the clouds settle from orange to purple, breathing slowly, and gently. I heard someone moving behind me, and I saw her, my Stella, and I was happy.

As the memory pressed itself into my chest, I stood, sweating under the cruel sun, the sweat at my lips was salty, and ran to my chin dripping. By the end of the evening, my work was done, and I had packed my bags, setting them in my buggy. I could hardly sleep, but the buggy would not run until the sun rose; I took my medicine, and I sat down in bed, I knew I would dream of her again tonight, and I could not wait to fall asleep.


\emph{In the morning, she rose, ate, gave thanks and left. I did not know where to, only that I would not see her again. The moisture traps were full, but that was not her job now. I waited until the sun went down, and then stopped waiting.}


On the 20th, I had made it out of the mouth of the valley, and set up camp under the stars, I took my food with my medicine, and I lay down, staring up at the million worlds my Dad used to tell me of. He had dreamed all of his life of taking me there with Mum, up to where the stars shone, and he had tried in love for so long. I was sure he was there now, with Mum, shining as he sleeps. Again I remembered Stella, the first time I had met her, and the stars in her eyes looking at me, so close. For those eyes, I gave her a name, and I am sure she liked it, resting under the soft pale yellow of the moon. When I awoke, the sun rose lazily, and the buggy sputtered with it's first life, and I began to pack.

On the 22nd, I could barely find the energy to make my tent, every second away from home felt like another thousand years packed onto my back. Aching, I lay down, poking my head out to look at the stars twinkling.  Yesterday I had been chased yellow grinning teeth, across the empty plains, and when my buggy went out, I stayed up through the dark, waiting for them to catch up. Once, with Stella, I had seen those teeth, as they threatened her and I. Not thinking, driven by fear, and anger I put an end to it with a knife tied to a stick. As the spotted thing panted roughly, life spilling through it's neck, it stared at me, and through ragged gasps breathed hate, it's eyes vicious, and unforgiving. I don't think Stella ever saw me the same after that. When exhaustion took me, my eyes were dark, and I slept a dreamless night. I awoke under the sun's zenith, and got into my buggy, another day gone.


\emph{The metal thing drove by, it smelt of sweat. I chased it, hidden, not wanting to be seen. Clearly it had seen me though, those of two legs were clever. I bode my time, but I could not catch up, and it passed out of my territory, onwards. I looked back to my business.}


On the 25th, I took the last of my medicine, and awoke the next day, knowing I could not return home. As I moved onwards though, the land beneath started to give, and the cracks receded. Not yet did I see trees, but I knew more than hoped, that soon I would see them, piercing the dull sky. On the 27th, I began to struggle, and the horizon blurred into the sky, all things turning blue. My joints crackled as I lay down to rest. Part of me cursed, I knew what would happen, that beyond the valley, age and death ruled, in truth, I knew I would be killing myself just to leave. But how bad could death be, life had never been that special, not without Stella.

 I stopped recording the days, and kept driving, the cracks once in the ground crept upwards, and down my arms. I thought back to Stella, who wore such wrinkles so naturally, that it hardly seemed to me like she was some wrinkly monster, I just wish I could have worn it as well as she. By the time I saw the tree, the buggy had dug itself deep into the mud below it, and I had to carry my things onwards, but what did that matter. Shaking in love and anticipation, I breathed deep and walked to the tree, my legs not yet giving out on me, and I sat against it, breathing in the air, and smelling the deep earth below me. I felt my cheeks drip with my love, and for a day I dared not move.
 
In truth, I never did move the buggy from that tree at all, I set up my camp, and explored around the oasis I had found on foot, reeds and berries, and trees, and damp earth. I waited there, eating and drinking what I had, content just to drink water from the ground, and to rest in grass. As the sun set on what I thought was the third day I had spent by the trees and the water, I thought again of Stella, and wept. Not in heartbreak that I would never see her, but in joy that I had known her, and that even out here, I felt warmed by the love she had given me. I slept easy, and the tears felt good, and I knew I would spend what time I had left here.


\emph{Some days after, I looked to a grey mass approaching, lumbering to and fro as the dust kicked up around her. By that time I stood only waveringly, unable to stop shaking. When she reached me, she stopped, wary of me, shaking her great white tusks, but weeping, I walked arms outstretched towards her. Then the moment came, I looked straight into the stars in her eyes, and recognition sparked, 50 years passed between us, and we were again under the stars, soaking in the waters next to the trees, even as the sun bore us down. I came up to her, and rubbed the dirt from her skin, hugging her tight, in those moments, there was no separation between us, I sang as she trumpeted, and we soaked in the water. Staring up at the dark sky, waiting for the stars to arrive, floating in the water, all those years washing away, I wondered why I hadn't done this sooner, why I had waited till my body broke, and I could hardly walk without medicine. All I knew, was that I was here now, seeing her one last time. I slept before the stars came.}