\emph{A twisted version of the Grimm fairytale Rumpelstiltskin, set in a steampunk city above the mysterious fey-inhabited wilds.}

The fey’s presence was cloying, and Princess Arachne of the Iron Towers was certain her throat was not the only dry one as it swept through the grand doors, bringing with it the creeping scents of wet moss and fungal decay. The most noticeable feature of the humanoid creature was the huge antlers that stretched from its head as if trying to scrape the ceiling above the silent subjects. The polished bone gleamed in the light of the chandeliers, projecting shadows of ghostly branches into the throne room. 

To her left, Arachne’s father, Magnate of the Iron Towers, shifted uncomfortably in his seat. She knew why; his was a world of metal and smoke, and whilst he may have held all the power in their city haven, the fey creature who hailed from the Wilds was in no way beholden to him. 

Arachne found herself unable to focus on its face. Her gaze slid away from the pale oval, into the mane of ivy vines that seemed to serve as hair, but she was left with a fleeting impression of deadly beauty. When she eventually managed to meet its eyes, she encountered twin pools of ink ringing pupils of green flame. Its feet were invisible beneath a swirling cloak of ruby leaves and brittle ashen branches, but they clicked hoof-like on the tiles as it prowled closer to the three thrones.  

To her right, Arachne’s mother, the ‘Keeper of the Fruits’, fruits that powered their world, was puffing her chest out. Arachne had noticed she often did this when nervous. It had amused the princess to learn that her mother’s fight or flight response was so similar to a feline puffing of fur. She would have found her parent’s attempts at bravado, faced with a magic they could never understand or aspire to control, entertaining. Instead, a heavy hopelessness weighed at her. 

A deal had been made, 20 years ago, when their meagre city was beginning to flourish with the magic of her parent’s inventions. The Wilds were dangerous, but as they fought to establish technology for the Towers, the city had faced loss after loss. The crux of the matter was that their power ran on the gases released from faerie fruits, harvested at great peril from the Wilds. The ancient fey who dwelled there hadn’t much liked that, but they had eventually agreed to leave the humans alone, in exchange for the firstborn child of the new town magnate and his wife, upon the eve of her 16th autumn solstice. It was an escape she had been longing for, and now it seemed it would never come to pass.

It wasn’t that Arachne disliked the Iron Towers. The twisting city of clockwork ingenuity was beautiful in a strange way, perched on a dais built high above the chaos of the Wilds, and defended by an ever-increasing arsenal of weapons she was responsible for designing. It had turned out the daughter of her city’s esteemed rulers had an inventive flair of her own. Arachne had discovered that the faerie fruit’s vapours were not their only useful properties. In extracting and harnessing the magical energy stored within the seeds, she had produced a weapon that would rip through any monster that dared scale their walls, and she’d been confined to her workshop ever since. Some subjects accused her of warmongering, others claimed her designs would be insufficient to protect them, and for her parents, she had become more of a resource than a daughter. The opportunity to leave, however unpredictable her destination, would have been a chance to prove their reliance on her, to finally earn the recognition she was owed for her work.

Her father rose first, though not in greeting.

“We have met your conditions, fey. We owe you nothing.”

“What conditions do you believe yourself to have met, mortal?” Arachne never saw its mouth move; in fact, she could not say for certain that the words ever graced the air with their presence. The creature’s voice seemed to scrape, rasping and yet harmonic, into the minds of those present. 

“You gave us three sunsets by which to find your name.” Indeed, as he spoke, the last glimmers of colour trickled from the stained-glass windows.

“In order to prevent you from taking our daughter, we have done the impossible, creature. We have learnt your name.”

Arachne could feel the fey’s grin in its sing-song reply, “And what do you suppose my name to be, mortal ruler.”

The magnate rose from his chair, just as Arachne sunk further down into hers, and spoke aloud the name he believed would put an end to this entire affair, and to her chances of a free life.

“Rumpelstiltskin.”

The fey stilled. Then the throne room filled with shaking shadows as it leant forwards, a choking cackle erupting from its twisted form. Arachne realised in shock that it was laughing, doubled over in apparent hysteria. The glamour over its visage seemed to shift and weaken, allowing the court to see a mouth of sharpened teeth open wider than any human jaws could extend. 

“I’m sorry. You think my name is…. Rumpelstiltskin?” The fey’s chuckling breaths smelt like autumn bonfires. 

“Your name is Rumpelstiltskin. We have found your name. We no longer have to adhere to your sick demands!” The magnate was yelling now, and Arachne almost shook her head at how quickly, in the face of panic, her father had forgotten his own teachings on court policy.

The fey straightened slowly up, and all present were subject to the chilling creak of sinister branches, before it raised a slim eyebrow. 

“Might I remind you that I am unable to lie, and so I mean this with the deepest sincerity: I am older than your most wizened elder and more powerful than your most dangerous, what were you calling them? ‘Faerie fruit’ weapons?”

Its vibrant green pupils seemed to flash as they turned towards Arachne. The princess forced a smirk to her face in place of fear, determined to focus on the acknowledgement of her creations, rather than how this creature could tear apart the throne room with a thought. 

“And you beheld, and thought, ‘this gentleman really looks like a Rumpelstiltskin’.” 

The creature’s mimicry was no patronising replication, but her father’s voice, exactly, echoing instead from the monster in front of them. The subjects gaped. The fey’s mouth stretched wide in a gash of a grin. 

“We were informed-” The magnate stammered.

“You were informed wrongly, it would seem.”

“But we were told-”

“-that I was seen dancing around a clearing singing my name for all the world to hear?”

A murmur spread around the subjects, as their leader stared, defeated, from a meaningless throne.

“Oh, don’t look so surprised,” it continued, “the mist can weave many mirages for the weary traveller, at my beck and call.”

“We won’t allow you to take our daughter!”

“Oh really? Don’t threaten to break a bargain with a fey, fool. The consequences of such a betrayal are not something your pitiful kingdom can withstand.” 

There was warning in its tone, but also excitement. It was daring them to go ahead and try it, Arachne thought. Her parent’s next argument came as a surprise, to her at least.

“We love her.”

The fey’s head tilted to a sickening angle, and the noise that echoed through the hall was at first the crackling of branches, then the crunching of bones. The magnate winced. Arachne watched in careful silence. 

“Is. That. So?” 

It drew each word out, and Arachne was distinctly reminded of a fly she had once seen trapped in the amber of the faerie fruits that had been delivered to her workshop. The golden treacle had dripped away from the preserved carcass with the same unnerving flow. Momentarily distracted by the fey’s tone, she did not immediately catch the implications of its question; it knew exactly how her parents measured her worth.

She finally spoke up, willing her voice into a cold cruelty, “I am necessary to this city.”

The fey turned, leering, towards her, and Arachne was certain only she heard its next words.

“Tell the truth, princess.”

Her hands clenched into white-knuckled fists, as she clarified, for all the court to hear, “My weapons are necessary to this city.” Releasing the ugly truth into the throne room brought no relief. The words tasted bitter on her tongue. 

“Well then, it will be curious to see how quickly it crumbles in the wake of your departure.” 

Arachne was loathe to admit it, but she had been wondering the same. 
