Long ago, when magic reigned and giants walked, a Sorcerer fell in love with a Princess. 

It happened suddenly and irrevocably, one frostbitten winter’s night. The Sorcerer had been travelling for months when he had come across an ancient and terrible castle far to the north, nestled among the mountains where the snow gathered and the forest drew closely in. While the castle had towers like black daggers and guards like wolves, the Sorcerer had powers beyond those of ordinary humans, and saw past the stony walls and thornwood gates to set eyes upon the Princess who lived inside. She was not especially beautiful nor especially wise, but Sorcerers do not feel as ordinary humans do, and he fell in love with her on the spot.  

The Princess had no idea she was being spied upon, and wouldn’t have cared too much even if she had known, because she was sitting by the bedside of her father the king, who was gravely ill. He was old and weary, and she no longer needed his guidance (being a strong and capable ruler herself) but she loved him and hated to see him suffer like this. In the light of the candles, her eyes (which were, peculiarly, an orange-gold colour) shone with suppressed tears. 

Very soon, it seemed, there would be a Queen in the castle. 

Night was falling thick and fast, just like the snow, so the Sorcerer approached the guards and asked if they would let a lonely traveller stay the night out of the cold. The guards, with their heavy swords and wolf-fur cloaks, looked him up and down and they didn't like what they saw.

"Do you have any skills or coin to repay the master of the castle for giving you shelter?" they asked him.

"Yes, I do," replied the Sorcerer immediately, who would have said anything for a chance to meet the Princess face-to-face. "I can heal your king as payment. In fact," he added, seized by inspiration, "that's the reason I'm here, actually: I heard he was ill and was so moved by his plight that I decided to come and see what I could do." 

The guards were suspicious but, after a brief discussion with each other, decided to give him the benefit of the doubt. After all, the Princess would skin them alive and hang them up for wall decor if she found out they had turned away a healer when her father lay dying. 

He was shown to the king’s chambers (when the Sorcerer saw the Princess, his heart jumped), where many of the king’s family and important nobles were gathered, and was given leave to heal him. It only took a few minutes of the Sorcerer murmuring complicated spells and making impressive hand-waving gestures before colour was restored to the king’s skin, his breathing eased and his eyes regained their former lustre.

A cry of joy went up in the room: it was obvious to everyone that the king was healed, and that the Sorcerer’s magic had worked. 

The king clasped the Sorcerer’s hand in his. “I cannot thank you enough for this,” he said, “I was sure this night would be my last. You must be rewarded: my daughter the Princess will see to it.” 

The Sorcerer looked at the Princess, as an excuse to trace his eyes over her feather-soft hair and orange-gold eyes. She smiled at him, and the Sorcerer almost fainted. 

Everyone left the elderly king to his rest and came into the Hall of the castle. The Princess took her place on the throne and asked the Sorcerer, “What is it you would like as a reward for your great service to my father?”

The Sorcerer stepped forward boldly and said, “My lady, I would beg of you the chance to be your suitor.”

There was a gasp like snow falling abruptly off a tree brough. Everyone else was staring at the Sorcerer with mixtures of offended shock and reluctant respect for his daring. 

“It would be unfair of me to grant you this, given that I cannot marry you,” said the Princess. 

The Sorcerer’s face fell. “Is there another man who has already won your heart? A noble lord, a prince, perhaps?” he asked.
 
"There is no man alive who loves me for who I am," the Princess said with a strange smile (the strange smile is important for later, take note), "They only love my wealth and lands." 

The Sorcerer threw himself onto his knees in front of her and clasped his hands to his heart. 

"But I love you," he cried, "I have loved you at first sight, and I couldn't imagine loving anyone else for the rest of my life. There is no one else in the world who loves you as much as I do!"

The Princess was a tadge embarrassed by this passionate show and tried to let him down gently without hurting his feelings. 

"That's very kind of you, really it is. I'm honestly flattered," she said, "But I think I'm going to have to say no." 

(Which was fair enough, in all honesty, given that she had only met the Sorcerer an hour ago.)

"What do you mean, 'no'?" 

"I mean what I say," replied the Princess, "I mean 'no'." 

The Sorcerer, who had been expecting the Princess to be delighted at her good fortune to have an exceedingly handsome and talented Sorcerer begging for her hand in marriage, felt suddenly furious. He sprang to his feet. How dare this Princess turn her nose up at him like he was beneath her? Right then and there, he decided to curse her with all of his power. 

He shouted out:– “For this slight, I curse you, cruel Princess! May you walk with a bumbling, clumsy gait; may your eyes freeze in their sockets; may you be covered in black spots, your memory fade, and your voice wither into shrieks! Indeed, may all your least important virtues be the only ones you have left!" 

There was a shocked, horrified silence in the hall. The Sorcerer realised he may have gotten a bit carried away in the heat of the moment, and hastily tacked onto the end:–  "That is, this curse will fall upon you if you do not spend midnight tonight with someone who loves you as much as I do.” 

(You may have noticed that the Sorcerer is a rather unstable fellow, so imagine how things would have turned out if he had married the Princess and had the opportunity to rule an entire kingdom.)

The Princess drew herself up and glared at the Sorcerer with more ice in her eyes than there was outside on the mountains. 

"Guards! Throw him out of the castle this instant!" she commanded, and there was the sound of twenty heavy swords being unsheathed as the guards advanced menacingly towards the Sorcerer. 

"You're making a terrible mistake!" the Sorcerer shouted, desperately.

The Princess looked down at him from the throne. "Oh, I don't think so," she said coolly. 

The guards marched the Sorcerer to the gate and threw him out into the night and the snow. In the sudden cold, the Sorcerer's temper began to cool, and he ran back to the gates to beg the guards to let him back in and make amends. But the guards weren't taken in by his change of heart and refused him. 

"Turn back, Sorcerer!" they shouted. "You have betrayed the trust of our lady and you are not welcome here!" 

They brandished thornwood spears that were soaked with the blood of all the hundreds of enemies who had fallen at the castle. But the Sorcerer was undeterred because the image of the Princess's face was still strong in his heart. 

For the second time, he approached the thornwood gates. 

"Turn back, Sorcerer!" shouted the guards. "You are not welcome here and will never be again – turn back!" 

They fired volleys of iron-tipped arrows sharp enough to cut air that missed the Sorcerer by a snowflake's breadth. Still he was undeterred. 

For the third time, the Sorcerer approached the thornwood gates. 

At that moment, to his profound shock, the guards all turned into ferocious wolves with white fangs and red tongues, and streamed towards him in an avalanche of claws and howls. The Sorcerer turned tail and ran for his life, all thoughts of casting a spell to save him flying out of his head in his all-consuming panic. 

The Princess watched him flee, before turning back to the anxious faces of her family and servants. 

“To bed, I think,” she said, smiling at them reassuringly. “It’s been a long day.”

Several worried looks and panicked frowns were exchanged. Her younger brother spoke up, “But… but, sister – the curse—” 

“Never you mind about the curse,” said the Princess, and dismissed them all with a wave of her hand.

Once they had gone, the Princess left the hall by a concealed staircase and ran up a set of turnpike stairs to reach a room at the very top of one of the castle’s towers, which was known as the “Room-Where-the-Aurora-Looks-In”. It was called this because every night when the aurora borealis shone and danced in the sky, some of the aurora’s light would get caught in that room, without fail, and set it aglow with purple or green or turquoise. That night, a sparkling emerald and a dazzling pink blush flowed over the walls of the Room-Where-the-Aurora-Looks-In. The Princess opened the window and dropped a silvercloth handkerchief out of it, the cold jaws of the night taking her breath away as she did so. 

The silvercloth handkerchief spun in the icy wind, once, twice, three times, like a swallow in a summer breeze, and then the light of the aurora fell squarely on the silver threads and the handkerchief lit up like a firework, a flash of brilliant emerald and pink against the coal-black sky. 

Then the wind snatched the handkerchief in its claws, and it vanished into the darkness of the night. 

Far below, in the castle yard, a silhouette saw this burst of light and stopped their work in front of the blacksmith’s forge. 

The Princess had smiled a strange smile when she had been asked if any man in the kingdom loved her because her true love wasn't a man. The fact of the matter was, the Princess had fallen in love with the Blacksmith's Daughter and both of them were planning to get married and run away together the following spring. 

That was why the Princess sent for the Blacksmith's Daughter that night, because that's how she would be able to avoid the Sorcerer's curse: all the conditions the Sorcerer had so rashly tagged on the end of his curse would be fulfilled if the Princess and the Blacksmith's Daughter spent midnight together… because they loved one another with the same fierce love the wind holds for the sky and the ice holds for the sea. 

The Blacksmith’s Daughter set down her tools, put the forge fire to sleep, and closed up the workshop as quietly and as quickly as frost forms on a windowpane. No one saw her approach the castle, nor the happiness in her eyes; no one heard the keys turned in the locks, nor the soft footfalls on the flagstones; no one noticed the doors silently swung to, nor the shadow rippling over the walls. 

But \emph{someone} was waiting for her in the Room-Where-the-Aurora-Looks-In, where jade and pink sapphire sparkled in the air. That was where the Princess and the Blacksmith’s Daughter met that night.  

By this time, the Sorcerer (you hadn't forgotten about him, had you?) was stuck up a pine tree with the twenty wolf-guards growling chillingly up at him from the tree's foot. The Sorcerer looked up at the night sky, and because he knew things that ordinary humans didn't know, he noticed it was almost midnight. He looked back at the castle with its dagger-like towers and saw the Princess and her lover clearly silhouetted against the aurora. The Sorcerer realised that the Princess had outwitted him and this time he was so angry all of his reason abandoned him in one overpowering avalanche of rage. He broke off a splinter of pine-wood from the tree he was clinging to and threw it with all of his might at the Princess and the Blacksmith's Daughter. 

Ordinarily, this wouldn't have achieved very much (given that the castle was half a mountain away), but remember: the Sorcerer had powers beyond those of ordinary humans, and the splinter of pine-wood flew through the wintry air with the speed and deadly precision of a crossbow bolt… and pierced deep into the heart of the Blacksmith's Daughter. 
 
A cry of deepest pain was wrenched from the breast of the Princess when she realised what had happened, and all the windows of the castle shattered at the sound. She pressed her hands to the wound hopelessly, feeling the warmth of the Blacksmith’s Daughter flowing out from under her fingers. 

Midnight struck. 

At that very moment, the Sorcerer’s curse crept into the Room-Where-the-Aurora-Looks-In. It saw what had happened: it saw the fading light in the eyes of the Blacksmith’s Daughter, the heartsick shock on the Princess’s face, the vicious, cruel weapon that the Sorcerer had thrown. The curse hesitated, and was surprised to feel a deep pity for the Princess. That morning, she had been sitting vigil by her father’s sick bed, and now, at night, she was at the side of another dying love. 

But a curse is still a curse, and cannot shirk its purpose. 

That’s why, some time later, two white shapes flew from the window of the Room-Where-the-Aurora-Looks-In. They were creatures of a sort that had never been seen before, creatures that had peculiar orange-gold eyes and spoke in shrieks and gurgles. If they had been walking, they would have walked with a bumbling, clumsy gait, and if they had wanted to look around, they would have had to turn their whole head. They were spotted with flecks of inky black, but had feathers as soft and as white as moonlight… 

The Princess and the Blacksmith’s Daughter had become the very first Snowy Owls.
