\begin{Puzzle}{22}{22}
|{} |{} |{} |{} |{} |{} |{} |{} |{} |[1]B |U |B |[2]B |L |[3]E |G |U |[3]M|.
|{} |{} |{} |{} |{} |{} |{} |{} |{} |{} |{} |{} |A|{} |{} |{} |{} |I |.
|{} |{} |{} |{} |[4]N |{} |[5]S |{} |{} |[6]A |N |A |R |C |H |Y |{} |R |.
|{} |{} |{} |{} |O |{} |E |{} |{} |{} |{} |{} |A |{} |{} |{} |{} |A |{} |[7]M |.
|[8]C |A |D |I |A |{} |L |{} |{} |{} |{} |{} |D |{} |{} |{} |{} |N |{} |A |.
|R |{} |{} |{} |H |{} |[9]D |E |A |T |H |{} |[10]D |O |M |E |S |D |A |Y |.
|E |{} |{} |{} |{} |{} |O |{} |{} |{} |{} |{} |U |{} |{} |{} |{} |A |* |A|.
|[11]T |H |E |R |M |O |N |[12]U |C |L |E |[13]A |R |{} |{} |{} |{} |{} |[14]T |.
|A |{} |{} |{} |{} |{} |{} |F |{} |{} |{} |L |{} |{} |{} |{} |{} |{} |H |.
|C |{} |{} |{} |{} |{} |[15]B |O |[16]R |G |{} |[17]D |E |A |T |H |S |T |A |R |.
|[18]E |L |D |A |[19]R |{} |{} |{} |E |{} |{} |E |{} |{} |{} |{} |{} |{} |N |.
|O |{} |{} |{} |E |{} |[20]B |{} |M |{} |{} |R |{} |[21]W |{} |{} |{} |{} |O |.
|U |{} |{} |{} |A |{} |O |{} |{} |{} |[22]F |A |M |I |N |E |{} |{} |S |.
|S |{} |{} |{} |P |{} |T |{} |{} |{} |{} |A |* |N |. 
|{} |{} |{} |{} |[23]E |X |T |E |[24]R |M |I |N |A |T |E |{} |{} |[25]Z |.
|{} |{} |[26]W |A |R |* |L |* |A |{} |{} |{} |{} |E |{} |{} |{} |O |{} |{} |{} |[27]E |.
|{} |{} |{} |{} |{} |[28]B |E |R |G |{} |[29]N |E |C |R |O |N |O |M |I |C |O |N |.
|{} |{} |{} |{} |{} |{} |C |{} |N |{} |{} |{} |{} |{} |{} |{} |{} |B |{} |{} |{} |T |.
|{} |{} |{} |{} |{} |{} |A |{} |A |{} |{} |{} |{} |{} |{} |{} |[30]S |I |G |M |A |R |.
|{} |{} |{} |{} |{} |{} |P |{} |R |{} |{} |{} |{} |{} |{} |{} |{} |E |{} |{} |{} |O |.
|{} |{} |{} |{} |{} |{} |{} |[31]C |O |N |Q |U |E |S |T |{} |{} |S |{} |{} |{} |P |.
|{} |{} |{} |{} |{} |{} |{} |{} |K |{} |{} |{} |{} |{} |{} |{} |{} |{} |{} |{} |{} |Y |.
\end{Puzzle}

\newcommand{\blnk}{\underline{\hspace{2em}}}

\newcommand{\cwclue}[4]{
% #1 - number
% #2 - answer
% #3 - question
% #4 - length
\item[\texttt{#1}] {{#3} ({#4})}
}
\hfill
\begin{minipage}[t]{0.45\textwidth}
\begin{center}{\large \altfont{Across}}\end{center}
\begin{small}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=0pt]
\cwclue{ 1}{BUBBLEGUM}{Sickeningly sweet, and princess of post-apocalyptic kingdom.}{9}
\cwclue{ 6}{ANARCHY}{The society without the guiding hand of our glorious Chair.}{7}
\cwclue{ 8}{CADIA}{Blew the fuck up, trying to keep Chaos at bay.}{5}
\cwclue{ 9}{DEATH}{Fourth Horsey Boy.}{5}
\cwclue{10}{DOMESDAY}{Thee olde timey namee fore apocalypse}{8}
\cwclue{11}{THERMONUCLEAR}{Makes the biiiiiig boooooom.}{13}
\cwclue{15}{BORG}{Likes technology, lives in cubes, kinda weird.}{4}
\cwclue{17}{DEATHSTAR}{Blew [13] the fuck up.}{9}
\cwclue{18}{ELDAR}{Almost caused the apocalypse in \emph{Warhammer 40K}}{5}
\cwclue{22}{FAMINE}{Third Horsey Boy.}{6}
\cwclue{23}{EXTERMINATE}{[3]'s catchphrase.}{11}
\cwclue{26}{WAR}{Second Horsey Boy.}{3}
\cwclue{28}{BERG}{Titanic's bane.}{4}
\cwclue{29}{NECRONOMICON}{Fictional(?) book for making friends at a graveyard.}{12}
\cwclue{30}{SIGMAR}{Age of \blnk, an often complained about version of \emph{Warhammer}.}{6}
\cwclue{31}{CONQUEST}{First Horsey Boy.}{8}
\end{itemize}
\end{small}
\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}
\begin{center}{\large \altfont{Down}}\end{center}
\begin{small}
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=0pt]
\cwclue{ 2}{BARADDUR}{Famous Ring-maker's Abode.}{8}
\cwclue{ 3}{MIRANDA}{One of our library's resident murderbots.}{7}
\cwclue{ 4}{NOAH}{Almost drowned a couple thousand years ago.}{4}
\cwclue{ 5}{SELDON}{Quite good at predicting the end of galactic empires.}{6}
\cwclue{ 7}{MAYA}{Predicted the apocalypse to be 10 years ago, apparently.}{4}
\cwclue{ 8}{CRETACEOUS}{$\flat$ Now the dinosaurs are gone. $\flat$}{10}
\cwclue{12}{UFO}{Visitors from another world, can only be filmed in grainy footage.}{3}
\cwclue{13}{ALDERAAN}{Blown the fuck up, just to prove a point.}{8}
\cwclue{14}{THANOS}{"Balanced, as all things should be."}{6}
\cwclue{16}{REM}{Rapid Eye Movement. Also a band.}{3}
\cwclue{19}{REAPER}{The Grim \blnk.}{6}
\cwclue{20}{BOTTLECAP}{Currency of the (post-apocalyptic) future!}{9}
\cwclue{21}{WINTER}{"\blnk is coming."}{6}
\cwclue{24}{RAGNAROK}{That one Chris Hemsworth movie where he tries to kill his sister, is enslaved and foments a revolution.}{8}
\cwclue{25}{ZOMBIES}{Classic Apocalypse}{7}
\cwclue{27}{ENTROPY}{Probably the most likely end of the universe.}{6}
\end{itemize}
\end{small}
\end{minipage}
\hfill
