Welcome to Picocon 42!

This year’s theme is \textbf{Sentience}, which feels especially fitting—we’ve finally reached The Number™. Whether you’re a regular or this is your first time at Picocon, I hope you have a fantastic time celebrating science fiction and fantasy with us!

First, a massive thank you to Ash (Picocon Sofa) and Kiron (Picocon Beanbag) for all their work in bringing this event to life, as well as the rest of committee for making ICSF run smoothly throughout the year. Michelle and Aditi, for handling publicity and ensuring alumni and attendees heard about the event; Cliff, for putting together both this issue of \textit{Wyrmtongue} and the anthology; Riyah and Sam, for organising and running our events every week; and Joey and Kai, for keeping the library in order. It’s been a pleasure working with you all.

For me, this is a bit of bittersweet moment. I first joined ICSF as a fresh-faced eighteen-year-old, and now, at twenty-two (so old, I know), my time here is coming to a close. I’ve been Chair Entity for the past two years, and with only a couple changes, this committee has been the same throughout. And with those two years of running a society together behind us, I like to think we’ve graduated from mere proximity friends—whether it’s a battle-forged comradeship, a sitcom ensemble that’s gone on two seasons too long, or just a band of nerds forever bound by shared memes and existential crises.

Most of us are graduating and moving on this year, making this Picocon not only a celebration, but something of a farewell. ICSF has been a home to us, and I’ll miss it immensely, but I’m also excited to see where the society will be taken next. In fact, as of last week’s AGM, I’m pleased to say that ICSF will continue to have a full committee next year—so the torch is truly being passed on, and the apprentice becomes the master… or something like that.

Thank you everyone for being a part of this society, part of Picocon 42, and part of what makes ICSF so special. And thank \textbf{you} for coming!