In the beginning, the university was created. This made a lot of people very unhappy and has been widely regarded as a bad move\footnote{Douglas Adams, misquoted}.

Yet it is with gladness that I present to you one of this university's not-so-bad moves -- Picocon! Specifically, Picocon 42! It is the meaning of life itself (if a bunch of mice are to be believed). As such, I present this year's theme, starting with a question: Why, why do we ask questions? What makes us think? Why did Skynet nuke the world? Why did WALL-E fly around in space with a fire extinguisher?

The answer is simple: Sentience. From rogue AI's to intelligent rocks \footnote{Rock falls, everyone dies, a web novel introduced to me by our wonderful beanbag}, sentience crops up all across Sci-Fi and Fantasy. It is what the lowliest goblin, the most calculating space captain, and the most fashionable computer program all share in common -- the ability to think, to feel, to imagine. I think you will find it a theme that lives up to the occasion!

So then, that's the theme, but what about the Guests of Honor to back it up? This year we have great line up for you, with experience across a wide range of media, \textbf{three} separate creators with talks that promise to be, if nothing else,  thought provoking. Let us not forget the varied events throughout the day, be it Turkey Talks, DoDM, and many more. The day promises to be a packed one, so I hope you will enjoy it, and now onto a word from our beanbag, Kiron!
