Ah, sentience. It is the long sought-after dream of this old editor \footnote{The editor is, as of writing, twenty-two.}. HOWEVER, even a mindless workdesk drone need not fear the dangers of getting lost in the schedule of a convention named after the pearl of electric dreams…

Throughout the morning, we have not one, but \emph{three} consecutive talks from our brilliant \emph{Guests of Honour}, who will give us insightful talks and discussions related to the nature of sentience, and perhaps even how to acquire it :$)$

After our minds have been nourished, so will our bodies, as lunch shall follow suit. There will be food available in the union, across the street at the \emph{Beir Bar}, so grab your snacks or grab a meal, the choice is yours\footnote{Or even better, ¿por qué no los dos?}!

Soon after, our rejuvenated bodies shall be used to fuel and enable the \emph{destruction of dodgy merchandise}. Participants will have to choose to save or obliterate questionable merchandise in a shower of steel and liquid nitrogen. Any resulting disputes can be settled in a noble custom known as \emph{baguette bash}. Only honour shall prevail. 

At 15:00, our guests will answer any prevailing questions about sentience in a \emph{Q\&A Panel}. This will soon be followed by \emph{Turkey Talks}, to balance out any intelligent thoughts that may have taken root from such thought provoking talks. The day shall end with the \emph{Picocon Quiz}, because brain teasers about pop culture and niche fandoms are essential to a healthy mind. 

As always, \emph{Imperial Tabletop Gaming} will return once more in \emph{Femtocon}. Be sure to check them out if you want to try out some fun boardgames! Those who wish brave the depths of science fiction and fantasy are always welcome to visit the \emph{Sci-Fi Library}, open lunchtimes throughout the week in Beit's West Basement.