Hello there.

Welcome to Picocon! And this time it’s in person! Which is a relief, as until only a month or so ago we weren’t sure if that would even be possible. I’d like to give a huge thanks to our excellent Picocon Sofa, Thomas, and our exquisite Picocon Beanbag, Peter, for putting together a world-endingly fun event under fairly significant time constraints! And a big thanks to the whole committee for their unrelenting hard work and dedication. Shockingly, this is my first in-person Picocon, and I’m therefore eagerly anticipating today as I hope many of you reading this will be!

I’d hope that this year has been good for the society, and I cannot overstate how brilliant it is to be able to regularly use the Sci-fi Library again. While the Discord server brought the library into the realm of the internet, the atmosphere and cosiness of our library is difficult to replicate. We’ve been making liberal use of it by hosting film nights on an almost weekly basis, including the entire extended edition Lord of the Rings films, the Dark Knight trilogy, and a marathon of every Spider-man film (R.I.P. Uncle Ben, gone but not forgotten). Furthermore, opening the library during lunchtimes has allowed people to borrow books from our rapidly overflowing shelves once again, and it’s wonderful to see the library being used as a proper library once more. I think this complements the Discord server quite well: with its many active alumni members, the society has a strong community sense both on and off campus, and long may it continue! After all, we never truly let you leave. We’re also definitely not a cult.

Before I go, I’d like to wish you all a good day! I will also shamelessly plug our AGM at 5PM on the 16th of March in the Sci-fi Library (please please please please please please someone run for chair please ok thanks). If you would like to talk with me, I will likely be kicking over cardboard boxes at the bottom of Lecture Theatre 1 as an outlet for the stress caused by my degree.