Last years original theme was initially planned to be apocalypse until we were forced to move the event online due to covid.

Bearing that in mind, and full of optimism for some chance of an in person event this year I thought we should return to the theme of Apocalypse and Dystopia and give it thought it deserved but missed out on last year. I have always found dystopian and apocalyptic fiction highly interesting, with characters forced into wildly extreme actions by the exceptional situations; and I hope you’ll find a lot of interest in the theme explored by talks from our excellent panel of authors.

With the success of running Picocon online last year we once again have authors from overseas joining us, AJ Flowers and Brendan Dubois joining us from North America to discuss their work and its relation to our themes of Apocalypse and Dystopia. Joining us in person we have Bryony Pearce and Louise Mumford whose talks will focus more on dystopian aspects as well as Gareth Powell and a shorter talk by Matthew Wraith. Following on from last year we are again streaming Picocon, and I am very thankful to have our tech-priest Anand making sure everything works and we don’t accidentally create skynet.

As well as the talks I’m particularly looking forward to our building and crushing of a cardboard town. Who doesn’t want to be godzilla smashing an apartment block? I guess all that’s left for me to say is a big thank you to the rest of the committee who have put in loads of work to make today great, and I hope you all have a wonderful time.
