Citizens of Imperial College, greetings and be welcome! I, your humble Chair Entity, extend a grand welcome to you all—both newcomers and seasoned travellers alike. Whether you arrived on the wings of a dragon, in a TARDIS, or merely took the Central Line, it is my honour to guide you through the gateway into the realm of the \textit{Imperial College Science Fiction and Fantasy Society}.

As the dawn of a new academic year rises, we invite you to join us in our sanctum: the \textit{Sci-Fi Library}. Nestled within the depths of the West Basement of Beit, it is a sanctuary crammed with a veritable dragon’s hoard — ten thousand books and three thousand DVDs spanning the farthest reaches of fiction, fantasy, and speculative worlds. Here, from \textit{12 to 2 pm on weekdays}, the doors stand open for all manner of activities: socialising, browsing, or simply relaxing before afternoon studies.

But that is not all! On \textit{Friday evenings}, we gather for legendary movie marathons, epic game nights, and seasonal festivity. For the cinema enthusiasts, our \textit{subsidised trips} to the latest film releases are the perfect chance to witness epic battles, interstellar voyages, and super-heroic deeds on the grandest of screens. And then there is \textit{Picocon} — our very own annual convention held in the second term!

To join this community of adventurers and time-traveling renegades, all you need do is purchase a membership, which grants you access to our subsidised cinema trips and the right to borrow from our vast collection.

So come, join us and be part of a fellowship that spans genres, galaxies, and realms — welcome, one and all, to the Imperial College Science Fiction and Fantasy Society!
