Tired of the Central Library? Come visit our second, smaller library in Beit's West Basement! As one of the university's oldest societies, we can boast amenities like no other.

\textbf{Lunchtime Showings} --- Want to kick up your feet and nerd out on a Friday night? We've always got plans - anything from games night, silly powerpoints, karaoke, or just putting on a movie from our extensive collection.

\textbf{Cinema Trips} --- Want to visit the cinema but find movie tickets too expensive? With our membership, cinema trip attendees pay less than £5. Follow our instagram or mailing list to see if anything interests you (see the \textbf{Getting Involved} section)!

\textbf{A Chill Time} --- Desperate for any opportunity to relax in Imperial's high-stress atmosphere? Me too, bestie.

As this year's Chair Of Vice, I hold responsibility for events - and what can I say? I believe in democracy. Stay engaged with ICSF through our various social media platforms or just pop by in person occasionally, and your opinions and suggestions for activities will be honoured. Enjoying science fiction and fantasy is for all, and we aim to step away from the boy's club stereotype to include all consumers of media, from the cultural phenomenon that is Twilight (marathon date TBD!) to yet another racially insensitive Dune adaptation (yes, we'll be organising a cinema trip when the next one comes out).

I'm also planning to rekindle a Sci-Fi tradition of yore: \textbf{the Sci-Fi annual trip}. Would you be interested in a weekend trip to "The Woodstock of the Mind" in Haye-on-Wye? Or would you prefer to rent a castle to live out your gothic dreams and nightmares over a long weekend? Let us know your thoughts!

I've run out of things to say. Goodbye. Swing by Sci-Fi and visit us sometime.