Hello there. I'm sure as many of you will know, we have a notable Picocon this year. Forty-Two! Most of you will recognise this number from Douglas Adams' \textbf{\emph{The Hitchhiker's Guide to The Galaxy}} (If you haven't yet, do give it a read! It's Sci-Fi Monty Python in book form). While we won't be answering any questions of life (or will we?), me and my wonderful assistant, our Picocon Beanbag Kiron Dutton, will be in charge of Picocon this year, and we hope not to disappoint. \\ \\
In any case, what does it mean for the theme of this year's Picocon? Well, why does the meaning of life even matter? What makes us ask such questions? In fact, how can we even \emph{think} about anything? What do Gollum, Luke Skywalker, Sam Vimes and Skynet all have in common? They are self aware. As such, the theme for \textbf{Picocon 42} is \textbf{Sentience}, the ability to experience feelings and sensations. The theme crops up all over Science Fiction and Fantasy, from eldritch beings that defy all understanding, to a cute little garbage compactor with a crush! \\ \\
Before I get too far ahead of myself, the freshers among us probably want to know what I'm actually talking about. Picocon is our society's annual convention, with talks from assorted authors and creators within the genre, charity fundraising, socialising, and fun activities. What other event in the year has baguette duels, insightful talks from guests of honour\footnotemark[3]{}, destruction of dodgy merchandise, and the recitation of cursed literature in the dreaded turkey talks\footnotemark[4]{}? It's all there, over just one day! And that day will be the \textbf{First of March}, don't miss it! \\ \\
And with that, my Wyrmtongue entry comes to a close, enjoy the term, and try not to let Imperial's eldritch knowledge drive you insane!