On behalf of Imperial College Science Fiction and Fantasy Society, I’d like to welcome everyone to Picocon 40: Twisted! 

I have to say I love the theme this year! We didn’t want to limit ourselves to Fantasy, or Science Fiction, so instead we have Twisted: a celebration of genre twists, media twists, and plot twists!

That being said, I think the biggest plot twist has been this convention coming together. It’s hard to believe that at the start of this academic year, we didn’t even have a Picocon Sofa or Beanbag, let alone a theme. But since being elected to these positions in November, Ernest and Riyah have gone from being first-time committee members, inspired by the single word ‘Twisted’, to running our 40th Picocon, the largest and most organised I’ve seen in my 3 years on committee! Special thanks should also go to our dedicated Picocon Cushions, Cliff and Irene, without whom all would be chaos. 

I’d also like to thank the rest of the ICSF Committee, all of whom have pitched in to help make Picocon great and keep me from descending into madness. Luke, Sophie, Toby, and Anand have sent countless emails, made orders, orchestrated technical magic, and just generally been willing to volunteer as tribute to help with everything Picocon. 

And what a Picocon it’s turned out to be, with 6 incredible guests spanning the media of books, films, and podcasts, all here to talk to you about the twists and turns of their work! I could write multiple paragraphs about their great works, and how excited we are to have them here, in-person and online, but that’s what the author description section of Wyrmtongue is for!

Now since I’m a final year student, this will technically be my last Picocon as a society and committee member (I mean, once an ICSF member, always an ICSF member, but I still won’t be allowed on committee from the great beyond), which means it’s obligatory for me to reminisce somewhat. I’ve loved running sci-fi events, first online for a year, and then back in glorious 4D, as the Chair of Vice, and now as Chairentity. It’s always great to hang out in the library at lunchtimes and Fridays, to make infinite book and TV recommendations, discuss whether the latest films were actually good for hours on end, and even just to take a break from The Degree. I’ve (cliché proximity alert meep meep meep) definitely made friends for life through this nerdy little basement-dwelling club!

(Fun Fact: I’m not the only one leaving, so please please please come along to our AGM on Friday to vote in next year’s committee or run yourself! Don’t let democracy die to thunderous applause!)

Thanks again to everyone who’s made this year at ICSF, and Picocon 40 in particular, more amazing than Spider-Man, and thank \textbf{\textit{you}} for joining us today (and apparently reading the entirety of my rambling)! 

Now go, be free, and enjoy Picocon 40: Twisted... 
