Greetings fellow friends, fans and fiends, and welcome to Picocon 40: Twisted!

To celebrate our triumphant return after the trials and tribulations of the pandemic,  I hope to revive this historic tradition with a bang!

As cliché as it sounds, a core tenant of good Sci-Fi and Fantasy is the subversion of expectations but not everyone considers the melodrama and effort it takes behind the scenes to bring our beloved stories to life. As such, the theme of Twisted was chosen to be as open to interpretation as possible, celebrating the personal spins that creators impart both on and off the page. 

I am very proud to present one of the most diverse cast of Guests of Honours yet, representing an unprecedented glimpse behind the curtain at some of our most beloved franchises. We have authors responsible for weaving entire universes, riveting podcasts and stunt choreographers breathing life into the silver screen. So, if you grew up on Worldweavers, want to explore the Broken Empire, get the scoop on Cocaine Bear, learn the intricacies of stage combat, debate the deep lore of the 41st Millennium or can't get enough of the Magnus Archives, Picocon 40 will blow your socks off.

Also, my eternal gratitude goes to the Picocon and Sci-Fi committee, especially to the incredible work done by Riyah and Rebecca in bringing all this to fruition. Of course, this event would be a far cry from possible without the efforts of the committee, from Sophie’s minutes to Luke’s budgeting to Anand’s techno-wizardry! Nor would these words even reach you without the work of the Wyrmtongue team.

As is tradition, the scavenger hunt and Destruction of Dodgy Merch as well as a plethora of side games make their triumphant return. If an afternoon spent smacking cursed merch around with a sledgehammer doesn’t sound like a good time, I don’t know what will. In the spirit of twisting traditions, we have also morphed the unspeakable… ichthyic tradition into: BAGUETTE BASH. I sincerely hope that you leave with the fond memory of gluten-filled duelling on our historic campus while the sun dramatically sets behind you. 

Have fun and thank you for being a part of this chapter in our history.
