\pagehead{Book Recommendations}

If you're looking to dive into the library's collection but are having
trouble deciding where to start, here are some recommendations from
the committee:

\bookrec{Ash Robson}{The Expanse Series}{James S A Corey}{Hard Sci-Fi with brilliant action, tense interplanetary politics, a hard-boiled detective, and of course a spooky alien virus. Couple that with some great writing and you can understand why I read the first book in a day and a night (sleep is for the weak!)}

\bookrec{Clifford Chan}{The Three Body Problem}{Liu Cixin}{The first of a mind bending hard sci-fi trilogy that won the Hugo Award in 2015. Also has a decent Netflix adaptation!}

\bookrec{Clifford Chan}{The Way of Kings}{Brandon Sanderson}{Beginning with the assassination of a king, this is a tale of a slave breaking free of his chains. One of Sanderson's greatest works to date, and the beginning of the Stormlight Archives. You're in for a storming treat.}

\bookrec{Clifford Chan}{The Grace of Kings}{Ken Liu}{Described as silkpunk fantasy, two brothers lead their seperate rebellions against the emperor of Dara. Inspired by real historical events, namely the Chu-Han Contention, this is a must-read for fans of epic fantasy.}

\bookrec{Clifford Chan}{The Wheel of Time series}{Robert Jordan}{At times tedious, this 14-book spanning story is one of gargantuan proportions. While rather trope-y, the series boasts great characters and a plot that, despite its meandering nature, reaches heights of awesome I didn't know was possible.}

\bookrec{Kai Lam}{The Fifth Science}{Exurb1a}{A whimsical look at the effects "the fifth science" has on the future of humankind. So good I'm giving my copy to the library so more people read it.}

\bookrec{Kai Lam}{His Dark Materials}{Philip Pullman}{Not a high-concept fantasy but with interesting philosophy and a great adventure.}

\bookrec{Kai Lam}{The Long Earth series}{Terry Pratchett and Stephen Baxter}{Great concept and execution, where it's possible to step into parallel worlds.}

\bookrec{Kai Lam}{Keys to the Kingdom Series}{Garth Nix}{A boy saves the universe story that I found a fun read.}